### 2021-10-25 doc/msp_code.tex
initial commit

\documentclass[18pt,a4paper]{extarticle}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{siunitx}
\usepackage{url}
\usepackage
[
a4paper,% other options: a3paper, a5paper, etc
left=1cm,
right=1cm,
top=1cm,
bottom=1cm,
% use vmargin=2cm to make vertical margins equal to 2cm.
% us  hmargin=3cm to make horizontal margins equal to 3cm.
% use margin=3cm to make all margins  equal to 3cm.
]
{geometry}

\author{Frank Hermann}
\title{Comparison of Radar Stations for MSP Measurements}

\DeclareMathOperator{\sgn}{sgn}
\renewcommand{\d}[1]{\ensuremath{\operatorname{d}\!{#1}}}
\setlength\parindent{0pt}

\begin{document}
\begin{center}
	\textbf{\Large{A Simple Radar Code for the Low Altitude Ionosphere}}\\
	\small{Frank Hermann, 24.10.2021}
\end{center}
\pagenumbering{gobble}
\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{code_diagram.pdf}
\end{figure}
We assume that the radar code $\epsilon$ is periodic $\epsilon_i = \epsilon_{i + L}$ and has already been transmitted for some time and that the radar continues transmitting the code indefinitely.
According to the sketch above, we see that
$$
\sum_{k=0}^{N-1} \epsilon_{i-k} V^{(k)}_i = m_i
$$
where $m_i$ is the $i$-th measured voltage and $N$ is the total number of range gates considered along the radar beam.
We calculate
$$
\langle \epsilon_{j + \Delta}m_{j + \Delta}^* \epsilon_j^*m_j\rangle = \epsilon_{j + \Delta}\epsilon_j^* \sum_{k=0}^{N-1} \epsilon_{j+\Delta-k}^*\epsilon_{j-k} \langle (V^{k}_{j + \Delta})^*V^{(k)}_j \rangle = \langle (V_{j+\Delta}^{(0)})^* V_j^{(0)} \rangle + \epsilon_{j + \Delta}\epsilon_j^*\sum_{k=1}^{N-1} \epsilon_{j+\Delta-k}^*\epsilon_{j-k} \langle (V^{k}_{j + \Delta})^*V^{(k)}_j \rangle
$$
where we have used the fact that signals from range gates of different altitudes do not correlate and assumed that $\epsilon_i^*\epsilon_i = 1$.
Furthermore, we have introduced $\Delta \in [1, M]$, where $M$ is the total number of measurement points in the auto correlation function.
Those will have the (desired) spacing of \SI{0.8}{\ms}.
The auto correlation function is defined as $\langle (V_{j+\Delta}^{(k)})^* V_j^{(k)} \rangle = R^{(k)}_\Delta$ assuming a wide sense stationary process for at least the time it takes to send the entire code once, which is $T = L\cdot\SI{0.8}{\ms}$.
We find for the auto correlation function of interest
$$
R^{(0)}_\Delta = \langle \epsilon_{j + \Delta}m_{j + \Delta}^* \epsilon_j^*m_j\rangle - \sum_{k=1}^{N-1} \epsilon_{j + \Delta}\epsilon_j^* \epsilon_{j+\Delta-k}^*\epsilon_{j-k} R_\Delta^{(k)}.
$$
In order to make the last term disappear we must average over the entire code to find the unbiased estimator
$$
\hat{R}^{(0)}_\Delta = \frac{1}{L}\sum^L_{j=1}\langle \epsilon_{j + \Delta}m_{j + \Delta}^* \epsilon_j^*m_j\rangle - \sum_{k=1}^{N-1}  R_\Delta^{(k)} \left[ \frac{1}{L} \sum^L_{j=1} \epsilon_{j + \Delta} \epsilon_j^*\epsilon_{j+\Delta-k}^*\epsilon_{j-k} \right]
$$
and demand that
$$
\frac{1}{L} \sum^L_{j=1} \epsilon_{j + \Delta} \epsilon_j^*\epsilon_{j+\Delta-k}^*\epsilon_{j-k} = 0.
$$
Due to technical limitations of the radar we have $\epsilon_i \in [-1, 1]$ and a naive brute force algorithm finds the following (shortest) codes for a given $N$ and $M$
\begin{center}
	\centering
	\begin{tabular}{cccc}
		\toprule
		$L$&$N$&$M$&Code\\
		\midrule
		24&5&4&$-+-+++++++-++--+-++-+++-$\\
		32&6&5&$-++-++++++++---++---+----++-+---$\\
		40&7&4&$-+--+++++++++-+++--+-+++----+-+++--++++-$\\
		\bottomrule
	\end{tabular}
\end{center}
However, a code with $N \cdot \SI{120}\km > H$ where $H$ is the total height of the ionosphere, is required.
\end{document}

### 2021-10-25 brute_code/code.c

@@ -1,0 +1,70 @@
+#include <iostream>
+#include <chrono>
+
+using namespace std;
+
+static const unsigned int N = 8, M = 4, maxL = 44;
+static const unsigned int minL = (max(N, M + 1) + 1)/2*2;
+
+typedef uint64_t code_t;
+
+void print(unsigned int L, code_t c){
+    for(unsigned int i = 0; i < L; i++){
+        if((c >> (L - i - 1)) & 1){
+            cout << "-";
+        }else{
+            cout << "+";
+        }
+    }
+    cout << endl;
+}
+
+void pyprint(unsigned int L, code_t c){
+    cout << "[";
+    for(unsigned int i = 0; i < L; i++){
+        if((c >> (L - i - 1)) & 1){
+            cout << "-1";
+        }else{
+            cout << "+1";
+        }
+        if(i != L - 1){
+            cout << ", ";
+        }
+    }
+    cout << "]" << endl;
+}
+
+__attribute__((optimize("unroll-loops"), always_inline)) inline void check(unsigned int L, code_t c){
+    code_t mask = (code_t(1) << L) - 1;
+    c = (c << L) | c;
+    for(unsigned int delta = 1; delta <= M; delta++){
+        code_t c0 = c ^ (c >> delta);
+        for(unsigned int k = 1; k < N; k++){
+            code_t c1 = c >> k;
+            code_t c2 = c >> (delta + k);
+            if(__builtin_popcountll((c1 ^ c2 ^ c0) & mask) != L/2){
+                return;
+            }
+        }
+    }
+    cout << "solution (L=" << L << "): ";
+    print(L, c);
+    pyprint(L, c);
+    exit(0);
+}
+
+int main(){
+    for(unsigned int L = minL; L <= maxL; L += 2){
+        cout << "L: " << L << endl;
+        auto start = chrono::system_clock::now();
+        #pragma omp parallel for
+        for(code_t c = code_t(1) << (L - 1); code_t(c) < (code_t(1) << L); c++){
+            check(L, c);
+        }
+        auto end = chrono::system_clock::now();
+        int elapsed = chrono::duration_cast<chrono::nanoseconds>(end - start).count();
+        if(elapsed > 0){
+            cout << "codes per sec " << 1000*((code_t(1) << L) - (code_t(1) << (L - 1)))/elapsed << "e6" << endl;
+        }
+    }
+}

### 2021-10-25 brute_code/code.c
optimization resulting in about (M^2 - M)/2 less popcnt instructions

@@ -3,7 +3,7 @@
 
 using namespace std;
 
-static const unsigned int N = 8, M = 4, maxL = 44;
+static const unsigned int N = 8, M = 4, maxL = 44; // we assume M < N
 static const unsigned int minL = (max(N, M + 1) + 1)/2*2;
 
 typedef uint64_t code_t;
@@ -37,9 +37,9 @@ void pyprint(unsigned int L, code_t c){
 __attribute__((optimize("unroll-loops"), always_inline)) inline void check(unsigned int L, code_t c){
     code_t mask = (code_t(1) << L) - 1;
     c = (c << L) | c;
-    for(unsigned int delta = 1; delta <= M; delta++){
+    for(unsigned int delta = 1; delta <= M; delta++){ // 181 machine instructions for code check at N = 8 and M = 4
         code_t c0 = c ^ (c >> delta);
-        for(unsigned int k = 1; k < N; k++){
+        for(unsigned int k = delta; k < N; k++){
             code_t c1 = c >> k;
             code_t c2 = c >> (delta + k);
             if(__builtin_popcountll((c1 ^ c2 ^ c0) & mask) != L/2){

### 2021-10-27 brute_code/code.c
optimization: we actually only need to check codes which start and end differently

@@ -3,7 +3,7 @@
 
 using namespace std;
 
-static const unsigned int N = 8, M = 4, maxL = 44; // we assume M < N
+static const unsigned int N = 4, M = 2, maxL = 44; // we assume M < N
 static const unsigned int minL = (max(N, M + 1) + 1)/2*2;
 
 typedef uint64_t code_t;
@@ -57,14 +57,15 @@ int main(){
     for(unsigned int L = minL; L <= maxL; L += 2){
         cout << "L: " << L << endl;
         auto start = chrono::system_clock::now();
-        #pragma omp parallel for
-        for(code_t c = code_t(1) << (L - 1); code_t(c) < (code_t(1) << L); c++){
+        //#pragma omp parallel for
+        for(code_t c = code_t(1) << (L - 1); code_t(c) < (code_t(1) << L); c += 2){
+            print(L, c);
             check(L, c);
         }
         auto end = chrono::system_clock::now();
         int elapsed = chrono::duration_cast<chrono::nanoseconds>(end - start).count();
         if(elapsed > 0){
-            cout << "codes per sec " << 1000*((code_t(1) << L) - (code_t(1) << (L - 1)))/elapsed << "e6" << endl;
+            cout << "codes per sec " << 500*((code_t(1) << L) - (code_t(1) << (L - 1)))/elapsed << "e6" << endl;
         }
     }
 }

### 2021-10-27 brute_code/code.c
removed debug print

@@ -59,7 +59,6 @@ int main(){
         auto start = chrono::system_clock::now();
         //#pragma omp parallel for
         for(code_t c = code_t(1) << (L - 1); code_t(c) < (code_t(1) << L); c += 2){
-            print(L, c);
             check(L, c);
         }
         auto end = chrono::system_clock::now();

### 2021-11-12 doc/msp_code.tex
add documentation to show that the code can be used to get information from a range for a range of altitudes at once

@@
 	\centering
-	\includegraphics[width=\linewidth]{code_diagram.pdf}
+	\includegraphics[width=0.9\linewidth]{code_diagram.pdf}
 \end{figure}
@@
 We calculate
-$$
-\langle \epsilon_{j + \Delta}m_{j + \Delta}^* \epsilon_j^*m_j\rangle = \epsilon_{j + \Delta}\epsilon_j^* \sum_{k=0}^{N-1} \epsilon_{j+\Delta-k}^*\epsilon_{j-k} \langle (V^{k}_{j + \Delta})^*V^{(k)}_j \rangle = \langle (V_{j+\Delta}^{(0)})^* V_j^{(0)} \rangle + \epsilon_{j + \Delta}\epsilon_j^*\sum_{k=1}^{N-1} \epsilon_{j+\Delta-k}^*\epsilon_{j-k} \langle (V^{k}_{j + \Delta})^*V^{(k)}_j \rangle
-$$
+\begin{align*}
+\langle \epsilon_{j + \Delta}m_{j + \Delta + h}^* \epsilon_j^*m_{j+h}\rangle &= \epsilon_{j + \Delta}\epsilon_j^* \sum_{k=0}^{N-1} \epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k} \langle (V^{(k)}_{j + \Delta})^*V^{(k)}_j \rangle\\
+&= \langle (V_{j+\Delta}^{(h)})^* V_j^{(h)} \rangle + \epsilon_{j + \Delta}\epsilon_j^*\sum_{k=0,k\neq h}^{N-1} \epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k} \langle (V^{(k)}_{j + \Delta})^*V^{(k)}_j \rangle
+\end{align*}
 where we have used the fact that signals from range gates of different altitudes do not correlate and assumed that $\epsilon_i^*\epsilon_i = 1$.
@@
 The auto correlation function is defined as $\langle (V_{j+\Delta}^{(k)})^* V_j^{(k)} \rangle = R^{(k)}_\Delta$ assuming a wide sense stationary process for at least the time it takes to send the entire code once, which is $T = L\cdot\SI{0.8}{\ms}$.
-We find for the auto correlation function of interest
+We find for the auto correlation function at height $h$
 $$
-R^{(0)}_\Delta = \langle \epsilon_{j + \Delta}m_{j + \Delta}^* \epsilon_j^*m_j\rangle - \sum_{k=1}^{N-1} \epsilon_{j + \Delta}\epsilon_j^* \epsilon_{j+\Delta-k}^*\epsilon_{j-k} R_\Delta^{(k)}.
+R^{(h)}_\Delta = \langle \epsilon_{j + \Delta}m_{j + \Delta + h}^* \epsilon_j^*m_{j+h}\rangle - \sum_{k=0, k\neq h}^{N-1} \epsilon_{j + \Delta}\epsilon_j^* \epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k} R_\Delta^{(k)}.
 $$
@@
 $$
-\hat{R}^{(0)}_\Delta = \frac{1}{L}\sum^L_{j=1}\langle \epsilon_{j + \Delta}m_{j + \Delta}^* \epsilon_j^*m_j\rangle - \sum_{k=1}^{N-1}  R_\Delta^{(k)} \left[ \frac{1}{L} \sum^L_{j=1} \epsilon_{j + \Delta} \epsilon_j^*\epsilon_{j+\Delta-k}^*\epsilon_{j-k} \right]
+\hat{R}^{(h)}_\Delta = \frac{1}{L}\sum^L_{j=1}\langle \epsilon_{j + \Delta}m_{j + \Delta + h}^* \epsilon_j^*m_{j + h}\rangle - \sum_{k=0, k \neq h}^{N-1}  R_\Delta^{(k)} \left[ \frac{1}{L} \sum^L_{j=0} \epsilon_{j + \Delta} \epsilon_j^*\epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k} \right]
 $$
-and demand that
+and demand that (with $W > w = k + H_1 - h + 1 > 0$ where $h \in [H_0, H_1]$ and $W=N+H_1 - H_0 + 1$)
 $$
-\frac{1}{L} \sum^L_{j=1} \epsilon_{j + \Delta} \epsilon_j^*\epsilon_{j+\Delta-k}^*\epsilon_{j-k} = 0.
+\frac{1}{L} \sum^L_{j=1} \epsilon_{j + \Delta} \epsilon_j^*\epsilon_{j+\Delta-w}^*\epsilon_{j-w} = 0.
 $$
-Due to technical limitations of the radar we have $\epsilon_i \in [-1, 1]$ and a naive brute force algorithm finds the following (shortest) codes for a given $N$ and $M$
+Due to technical limitations of the radar we have $\epsilon_i \in [-1, 1]$ and a naive brute force algorithm finds the following (shortest) codes for a given $W$ and $M$
 \begin{center}
@@
 		\toprule
-		$L$&$N$&$M$&Code\\
+		$L$&$W$&$M$&Code\\
 		\midrule
@@
 \end{center}
-However, a code with $N \cdot \SI{120}\km > H$ where $H$ is the total height of the ionosphere, is required.
+Note that for $H_1 = H_0 = 0$ we can use that $k\neq h$ and find $W=N$.
 \end{document}

### 2021-11-12 doc/msp_code.tex
improved doc: a N code is actually usable at all altitudes, due to its shift invariance

@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{code_diagram.pdf}
+	\includegraphics[width=0.8\linewidth]{code_diagram.pdf}
 \end{figure}
@@
 The auto correlation function is defined as $\langle (V_{j+\Delta}^{(k)})^* V_j^{(k)} \rangle = R^{(k)}_\Delta$ assuming a wide sense stationary process for at least the time it takes to send the entire code once, which is $T = L\cdot\SI{0.8}{\ms}$.
-We find for the auto correlation function at height $h$
+We find for the auto correlation function at height $h \in [0, N-1]$
 $$
@@
 $$
-and demand that (with $W > w = k + H_1 - h + 1 > 0$ where $h \in [H_0, H_1]$ and $W=N+H_1 - H_0 + 1$)
+and demand that (with $w = k - h \neq 0$ so that $|w| < N$)
 $$
@@
 $$
-Due to technical limitations of the radar we have $\epsilon_i \in [-1, 1]$ and a naive brute force algorithm finds the following (shortest) codes for a given $W$ and $M$
+Due to technical limitations of the radar we have $\epsilon_i \in [-1, 1]$ and a naive brute force algorithm finds the following (shortest) codes for a given $N$ and $M$
 \begin{center}
@@
 		\toprule
-		$L$&$W$&$M$&Code\\
+		$L$&$N$&$M$&Code\\
 		\midrule
@@
 \end{center}
-Note that for $H_1 = H_0 = 0$ we can use that $k\neq h$ and find $W=N$.
+Note that we have used that every code which is valid for $w$ is also valid for $-w$, because the value of the sum does not change if the code is shifted by $w$, due to the codes periodicity.
 \end{document}

### 2021-11-25 brute_code/code.c
add some code inline comments

@@ -3,11 +3,14 @@
 
 using namespace std;
 
-static const unsigned int N = 4, M = 2, maxL = 44; // we assume M < N
+static const unsigned int N = 6, M = 3, maxL = 44; // we assume M < N
 static const unsigned int minL = (max(N, M + 1) + 1)/2*2;
 
 typedef uint64_t code_t;
 
+/*
+ * print code in +- format
+ */
 void print(unsigned int L, code_t c){
     for(unsigned int i = 0; i < L; i++){
         if((c >> (L - i - 1)) & 1){
@@ -19,6 +22,9 @@ void print(unsigned int L, code_t c){
     cout << endl;
 }
 
+/*
+ * print code in python array format
+ */
 void pyprint(unsigned int L, code_t c){
     cout << "[";
     for(unsigned int i = 0; i < L; i++){
@@ -34,19 +40,29 @@ void pyprint(unsigned int L, code_t c){
     cout << "]" << endl;
 }
 
+/*
+ * Checks if the given code is valid. If yes, it is printed and the program is
+ * exited.
+ */
 __attribute__((optimize("unroll-loops"), always_inline)) inline void check(unsigned int L, code_t c){
     code_t mask = (code_t(1) << L) - 1;
     c = (c << L) | c;
+    // when checking the machine code make sure that these loops are unrolled
+    // and that this function is inlined
     for(unsigned int delta = 1; delta <= M; delta++){ // 181 machine instructions for code check at N = 8 and M = 4
         code_t c0 = c ^ (c >> delta);
         for(unsigned int k = delta; k < N; k++){
             code_t c1 = c >> k;
             code_t c2 = c >> (delta + k);
+            // the following machine instruction calculates the sum over the bitvector
+            // if it is not supported, it must be implemented in software which
+            // will come with a large performance impact
             if(__builtin_popcountll((c1 ^ c2 ^ c0) & mask) != L/2){
-                return;
+                return; // code not valid
             }
         }
     }
+    // if we get here, the code is valid
     cout << "solution (L=" << L << "): ";
     print(L, c);
     pyprint(L, c);
@@ -54,10 +70,12 @@ __attribute__((optimize("unroll-loops"), always_inline)) inline void check(unsig
 }
 
 int main(){
+    // loop over bitvector length
     for(unsigned int L = minL; L <= maxL; L += 2){
         cout << "L: " << L << endl;
         auto start = chrono::system_clock::now();
-        //#pragma omp parallel for
[…]

### 2022-03-03 doc/msp_code.tex
add more codes
update documentation

@@
 \usepackage{listings}
+\usepackage{hyperref}
 \usepackage{siunitx}
 \usepackage{url}
-\usepackage
-[
-a4paper,% other options: a3paper, a5paper, etc
-left=1cm,
-right=1cm,
-top=1cm,
-bottom=1cm,
-% use vmargin=2cm to make vertical margins equal to 2cm.
-% us  hmargin=3cm to make horizontal margins equal to 3cm.
-% use margin=3cm to make all margins  equal to 3cm.
-]
-{geometry}
 
 \author{Frank Hermann}
-\title{Comparison of Radar Stations for MSP Measurements}
+\title{Radar code documentation}
 
@@
 \begin{document}
-\begin{center}
-	\textbf{\Large{A Simple Radar Code for the Low Altitude Ionosphere}}\\
-	\small{Frank Hermann, 24.10.2021}
-\end{center}
-\pagenumbering{gobble}
-\begin{figure}[h!]
+\maketitle
+\begin{figure}
 	\centering
-	\includegraphics[width=0.8\linewidth]{code_diagram.pdf}
+	\includegraphics[width=1\linewidth]{code_diagram.pdf}
+	\caption{Range time diagram of the simplified version of the radar code.}
+	\label{fig:sketch}
 \end{figure}
-We assume that the radar code $\epsilon$ is periodic $\epsilon_i = \epsilon_{i + L}$ and has already been transmitted for some time and that the radar continues transmitting the code indefinitely.
-According to the sketch above, we see that
-$$
+
+\section{Introduction}
+A binary phase radar code is presented which has optimal noise canceling properties, intrinsically measures the entire range at once (assuming that it is finite) and supports arbitrary radar duty cycles.
+\section{Mathematical description}
+We assume that the radar code $\epsilon$ has length $L$ and is periodic $\epsilon_i = \epsilon_{i + L}$.
+Furthermore, the radar code is normalized and binary phase, meaning that $\epsilon_i \in [-1, 1]$.
+This implies that $\epsilon_i^*\epsilon_i = 1$, where we could drop the complex conjugate symbol, but we will keep it to show that the formalism also applies to poly-phase codes.
+We further assume that the radar code is transmitted indefinitely.\\
+Figure \ref{fig:sketch} illustrates the measurement process of the unmodulated code.
+In the figure, it can be seen that the measured voltage $m_i$ at time index $i$ can be calculated by summing over the scattered voltages $V^{(k)}_i$ which are modulated with the radar code,
+\begin{equation}
 \sum_{k=0}^{N-1} \epsilon_{i-k} V^{(k)}_i = m_i
-$$
-where $m_i$ is the $i$-th measured voltage and $N$ is the total number of range gates considered along the radar beam.
-We calculate
-\begin{align*}
-\langle \epsilon_{j + \Delta}m_{j + \Delta + h}^* \epsilon_j^*m_{j+h}\rangle &= \epsilon_{j + \Delta}\epsilon_j^* \sum_{k=0}^{N-1} \epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k} \langle (V^{(k)}_{j + \Delta})^*V^{(k)}_j \rangle\\
-&= \langle (V_{j+\Delta}^{(h)})^* V_j^{(h)} \rangle + \epsilon_{j + \Delta}\epsilon_j^*\sum_{k=0,k\neq h}^{N-1} \epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k} \langle (V^{(k)}_{j + \Delta})^*V^{(k)}_j \rangle
-\end{align*}
-where we have used the fact that signals from range gates of different altitudes do not correlate and assumed that $\epsilon_i^*\epsilon_i = 1$.
-Furthermore, we have introduced $\Delta \in [1, M]$, where $M$ is the total number of measurement points in the auto correlation function.
-Those will have the (desired) spacing of \SI{0.8}{\ms}.
-The auto correlation function is defined as $\langle (V_{j+\Delta}^{(k)})^* V_j^{(k)} \rangle = R^{(k)}_\Delta$ assuming a wide sense stationary process for at least the time it takes to send the entire code once, which is $T = L\cdot\SI{0.8}{\ms}$.
-We find for the auto correlation function at height $h \in [0, N-1]$
-$$
-R^{(h)}_\Delta = \langle \epsilon_{j + \Delta}m_{j + \Delta + h}^* \epsilon_j^*m_{j+h}\rangle - \sum_{k=0, k\neq h}^{N-1} \epsilon_{j + \Delta}\epsilon_j^* \epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k} R_\Delta^{(k)}.
-$$
-In order to make the last term disappear we must average over the entire code to find the unbiased estimator
-$$
-\hat{R}^{(h)}_\Delta = \frac{1}{L}\sum^L_{j=1}\langle \epsilon_{j + \Delta}m_{j + \Delta + h}^* \epsilon_j^*m_{j + h}\rangle - \sum_{k=0, k \neq h}^{N-1}  R_\Delta^{(k)} \left[ \frac{1}{L} \sum^L_{j=0} \epsilon_{j + \Delta} \epsilon_j^*\epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k} \right]
-$$
-and demand that (with $w = k - h \neq 0$ so that $|w| < N$)
-$$
-\frac{1}{L} \sum^L_{j=1} \epsilon_{j + \Delta} \epsilon_j^*\epsilon_{j+\Delta-w}^*\epsilon_{j-w} = 0.
-$$
+\end{equation}
+where $N$ is the maximum altitude index considered and $k$ is the altitude index.
+Note that $N$ must be finite.\\
+Now, the estimator
+\begin{equation}
+\hat{R}^{(h)}_\Delta = \frac{1}{L}\sum^L_{j=1}\epsilon_{j + \Delta}m_{j + \Delta + h}^* \epsilon_j^*m_{j + h}.
+\end{equation}
+for the autocorrelation function $R$ at altitude $h$ and lag $\Delta$ is considered.
+In the following, it will be shown that this estimator is unbiased, if the code fulfills a certain condition.\\
+We calculate the expectation value of the estimator
+\begin{equation}
+\langle \hat{R}^{(h)}_\Delta \rangle
+=\frac{1}{L}\sum^L_{j=1} \epsilon_{j + \Delta}\epsilon_j^* \sum_{k=0}^{N-1} \epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k} \langle (V^{(k)}_{j + \Delta})^*V^{(k)}_j \rangle
+\end{equation}
+where the double sum was reduced to a single sum symbol, because scattered voltages of different altitudes do not correlate.
+Now, we use the definition of the autocorrelation function $\langle (V_{j+\Delta}^{(k)})^* V_j^{(k)} \rangle = R^{(k)}_\Delta$, where we assume a wide sense stationary process during the time it takes to transmit the code once.
+\begin{equation}
+\langle \hat{R}^{(h)}_\Delta \rangle
+= R^{(h)}_\Delta + \sum_{k=0,k\neq h}^{N-1}R^{(k)}_\Delta
+\left[ \frac{1}{L}\sum^L_{j=1}\epsilon_{j + \Delta}\epsilon_j^* \epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k}\right].
+\end{equation}
+The estimator is unbiased if the expression in the square brackets is zero.
+Let $w = k - h$ and note that $w \neq 0$ and $|w| < N$.
+Using the periodicity it can be shown that the condition is equivalent to
+\begin{equation}
+0 = \frac{1}{L}\sum^L_{j=1}\epsilon_{j}\epsilon_{j+w}^* \epsilon_{j+\Delta}^*\epsilon_{j + \Delta + w}.
+\label{eq:cond}
+\end{equation}
+In the next section, solutions of this equation are discussed.
+
+\section{Solving the code condition}
+The condition given by \eqref{eq:cond} is trivially fulfilled for pseudo random numbers if $L \rightarrow \infty$.
+However, the measurement would have no (definitive) time resolution in this case.
+With a brute-force computer search it can be shown that solutions do exist, when a finite $\Delta \in [1, M]$ is assumed, where $M$ is the total number of measurement points in the auto correlation function.
+If a code fulfills the condition it will be referred to as a valid code.
+Note that an inversion or a (cyclic) shift of any valid code is also a valid code.
+Thus, only codes which start with a $+$ (or $-$) must be checked.
+Further, all codes which do not contain the sequence $+-$ must be a constant sequence.
+Thus is sufficient to check codes which start with $+$ and end with $-$.
+However there are still many codes which are cyclic versions of other codes.
+
+\subsection{Number of codes}
+For each $L$ periodic code, there are $L$ shifted versions, but how many $L$ periodic codes are there?
+If $L=6$ there are also $2^3$ $3$-periodic codes and $2^2$ $2$-periodic codes.
+However, in both cases we must subtract the amount of $1$ periodic codes, yielding the recursive equation
+\begin{equation}
+N_6 = 2^6 - N_3 - N_2
+\end{equation}
+where $N_L$ is the number of $L$ periodic codes.
+The general equation is
+\begin{equation}
+N_L = 2^L - \sum_{i \in D(L)} N_i
+\end{equation}
+where $D(L)$ is the set of even divisors of $L$.
+
+\subsection{Building the codes}
+We will introduce the compressed notation of a code here.
+For example: 11001110 is 2231 in the compressed notation.
+We want to generate codes which do not
+\begin{enumerate}
+	\item have a periodicity smaller than $L$,
+	\item exist multiple times as shifted versions and
+	\item exist another time as inverted version.
+\end{enumerate}
+If we generate a code from its compressed version we can ensure the last condition by starting always with $-$ (or $+$).
+To ensure (2) we must realize that the number of digits in the compressed version must also be even so that the code does not start and end with the same sign.
+Furthermore, any code has a longest sequence $\omega$ of ones.
+In the case that the code contains a sequence of zeros longer than the longest sequence of ones, we consider its inverse.
+We can always place this sequence at the beginning, which means that in the compressed version the largest digit always comes first.
+However, a sequence of length $\omega$ might occur multiple times in the code, which can lead to a violation of (1).
+The solution is to split the code so that each sub-sequence starts with $\omega$ and the digits which follow are itself a sequence of the type discussed here.
+
+6
+51
+42
+33
+2211
+111111
+
+\subsection{The autocorrelation of a code}
+
+Let
+\begin{equation}
+\gamma_{j, i} = \epsilon_{j + i}^*\epsilon_{j}
+\end{equation}
+so that the autocorrelation function of the code can be written as
+\begin{equation}
+s_i = \sum_{j=1}^{L}\gamma_{j, i}.
+\end{equation}
+We want to satisfy conditions of the type $s_i=0$ for certain values of $i$, which requires solving the inverse problem, which is, calculating $\epsilon$ given a certain $\gamma$.
+The recursive equation
+\begin{equation}
+\epsilon_{j + i}^* = \gamma_{j, i} \epsilon_{j}
+\end{equation}
+follows directly from the definition of $\gamma$.
+It can be solved by plugging it into itself till $\epsilon_j$ is encountered again, which yields the following condition for the existence of a solution
+\begin{equation}
+\gamma_{k, i} = \prod_{j=1}^{L/d - 1}\gamma_{jd + k, i}
+\end{equation}
+where $d=d(i)$ is the greatest common denominator of $L$ and $i$ and $k \in [1, d]$.
+Thus, we have $d$ conditions, which removes $d$ degrees of freedom from $\gamma_{j, i}$, meaning that for each value of $i$, a number of $L-d$ bits can be chosen arbitrarily without violating the condition above.\\
+We have now formally solved the problem for a single, fixed value of $i$.
+In order to satisfy a problem in which two values of $i$ are allowed, called $i_1$ and $i_2$, we calculate the sets of corresponding solutions $\gamma_{j, i}$ and $\gamma'_{j, i'}$ first.
+
+\begin{equation}
+s'_i s_i = \sum_{j'=1}^{L}\sum_{j=1}^{L}\gamma'_{j', i}\gamma_{j, i}.
+\end{equation}
+
+\subsection{Connections between $\gamma$}
+\begin{equation}
+\gamma_{j, i_1}\gamma_{j, i_2} = \epsilon_{j + i_2}^*\epsilon_{j}\epsilon_{j + i_1}^*\epsilon_{j} = \gamma_{j+i_1, i_2-i_1}
+\end{equation}
+\begin{equation}
+\gamma_{j+i, i}\gamma_{j, i}=\gamma_{j, 2i}
+\end{equation}
+\newpage
+if the code did not have a sequence 111 it is not necessarily periodic, but it must be under the condition that there is a balance of positive and negative contributions to the sum
+
+in compressed form each digit must be smaller than 3
+111111111111212122222211
+because we must fulfill $\Delta = w = 1$ 1X1 contributes +1, 12 and 21
+
+in a simple compressed form two adjacent 0 symbols are not allowed
+101010100
+111111101
+
+01: 10, 0
+10: 1, 01
+
+no optimization $2^6$
+with double one in the beginning $2^4$
+6
+51
+42, 411 (411 not valid! (cyclic shift))
+321, 312 (not valid! cyclic shift!), 3111
+21111
+111111
+with cyclic elimination $2^3$
+8
+3221, 3122, 3212, 31121
+
+31122312
+
+in a code of length $L$ are $2^{N-m+1}$ combinations with $m$ or more equal bits in a row. this
+
++-+-++-+++
+
+fourie like decomposition (walsh matrices?)
+
+decomposition into products of codes (advantage: stays on ring)
++++++- => +++++-
+++++-- => ++++--
++++--- => +++-+-
+++---- => ++-+--, ++--+-
++----- => +-+-+-
+each row is only allowed to combine (by multiply) with uneven number of rows above it
+
+different approach: build each code out of periodic codes, for example take a 3 and a 2 periodic code, will have maximum periodicity of 6
++-+-+- (1 periodicity)
+++--++ (2 periodicity)
++--+--, +++--- (3 periodicity)
+
++----+----, ++---++---, +++++---- (5 periodicity for L=10)
+
+there are even and uneven n-periodicity codes or should we change the definition of periodicity?
+
+n periodicity times m periodicity code is a n*m periodicity code
+
+If $\epsilon_i = \epsilon_{i+j}$ we will call the code $j$ periodic, thus
+$\epsilon_i\epsilon_{i+nj} = 1$
+
+when code has length L, the code can NOT be expressed as a product of codes which lengths are the prime factors of L.
+
++-+-+- (2)
+++-++- (3)
++---++ (6)
+
+++-- (satisfies j=1)
+
+solutions for even j can be constructed easily
++++- (satisfies j=2)
++++-++-+ (satisfies j=4)
++-+--+-+
+how can they be joined? simple multiplication???
+
+the code +---- is already a basis for all codes of the same length
+
+take a look at period discrete convolution
+
+\begin{equation}
+a_{i_1}b_{i_2}a_{i_1+j}b_{i_2+j}
+\end{equation}
+
+\begin{equation}
+s_j = \sum_{i=1}^{L} a_i a_{i+j} = -L
+\end{equation}
+if $a_i$ is $j$ periodic
+
+\begin{equation}
+s_j = \sum_{i=1}^{L} a_ib_i a_{i+j} b_{i+j} = - \sum_{i=1}^{L} b_i b_{i+j}
+\end{equation}
+if $a$ is $j$ periodic, thus it is not necessary to consider any $j$ periodic components if $s_j=0$ is demanded.
+\begin{equation}
+s_j = \sum_{i=1}^{L} (a_i + a_{i+j})^2 b_i  b_{i+j} = - \sum_{i=1}^{L} b_i b_{i+j}
+\end{equation}
+
+\begin{equation}
+s_j = \sum_{i=1}^{L} \epsilon_i \epsilon_{i+j} = \sum_{i=1}^{L} |\epsilon_i + \epsilon_{i+j}| - 1 \geq 2 W - L
+\end{equation}
+
+\begin{equation}
+W = \sum_{i=1}^{L} \epsilon_i \leq (s_j + L)/2
+\end{equation}
+
+\section{Modulating the code}
+
+\section{Code with cyclic difference set for $\tau_i$}
+
+\section{Properties of the code}
+
+\section{Simulation}
+\subsection{Monte Carlo Generation}
+The most straight-forward approach to generate random numbers following a wide-sense stationary process is as follows:
+\begin{equation}
+R^{(h)}_{jk} = \langle (V_{j}^{(h)})^* V_k^{(h)} \rangle
+\end{equation}
+where $R^{(h)}_{jk}$ is interpreted (for some fixed $h$) as a correlation matrix for the random vector $V_{j}^{(h)}$ which is to be generated.
+We can satisfy the correlation properties by a linear transformation
+\begin{equation}
+V_j^{(h)} = \sum_{i} T_{ji}f_i
+\end{equation}
+where $T_{ji}$ must be of toeplitz type and $f_i$ are uncorrelated standard normal Gaussian circular-symmetric random variables with $\langle f_i f_j \rangle = \delta_{ij}$.
+This yields
+\begin{equation}
+R^{(h)}_{jk} = \sum_{i,l} \langle (T_{ji}f_i)^* T_{kl}f_l \rangle = \sum_{i} T_{ji}^* T_{ki}.
+\end{equation}
+Using that the matrix $T$ is symmetric and seeing that $R^{(h)}_{jk}$ must be positive semidefinite (as it is a covariance matrix) we can calculate $T$ with some square root of matrix algorithm.\\
+However all of this can be done more efficiently by using the time stationary of the process.
+Note that $T$ is of toeplitz type simply means that we actually need a convolution of $f$ with $T$ where $T$ must be symmetric with a length of at least $2M + 1$ so that the points up to $M + 1$ can be correlated.
+However, the generated time series would not have the true correlation properties of the ACF if it is truncated after $M+1$.
+The ACF can be either truncated after $n-1$, where $n$ is the total length of the time series, or when the ACF approaches approximately zero.
+Now, denote the length of the ACF by $K$.
+The convolution is given by
+\begin{equation}
+V_j^{(h)} = \sum_{i=1-K}^{K-1} T_{i}f_{j - i}.
+\end{equation}
+It follows that,
+\begin{equation}
+R^{(h)}_{jk} = \langle (V_{j}^{(h)})^* V_k^{(h)} \rangle = \sum_{l=1-K}^{K-1} \sum_{m=1 - K}^{K-1} T_{l} T_{m} \langle f_{j - l} f_{k - m} \rangle.
+\end{equation}
+Using that $\langle f_{j - l} f_{k - m} \rangle = \delta_{m, k - j + l}$ and substituting $\Delta=j-k$ yields
+\begin{equation}
+R^{(h)}_\Delta = \sum_{i=1-K}^{K-1} T_{i} T_{i - \Delta}
+\end{equation}
+where it is assumed that $T$ is zero padded for all indices which fall out of range.
+Applying a Fourier transform over $\Delta$ on both sides results in
+\begin{equation}
+\mathrm{DCT}[R^{(h)}]_j = \sum_{i=1-K}^{K-1} T_{i}\mathrm{DTFT}[T_{i - \Delta}]_j.
+\end{equation}
+From the definition of the $\mathrm{DTFT}$ follows that
+\begin{equation}
+\mathrm{DCT}[R^{(h)}]_j = \sum_{l=1-K}^{K-1} T_{l}\exp\left(\frac{i2\pi lj}{2K-1} \right) \mathrm{DCT}[T]_j,
+\end{equation}
+using the definition of the Fourier transform again results in
+\begin{equation}
+\mathrm{DCT}[R^{(h)}]_j = (2K - 1)\left( \mathrm{DCT}[T]_j \right)^2.
+\end{equation}
+Now there are two options: Either one solves for $T$ and does the convolution in the time domain, or one solves for the Fourier transform of $T$ and does the convolution in Fourier space.
+Which one is faster depends on the choice of $K$.
+The first approach is preferred when $K$ is fixed which results in an asymptotic runtime of $\mathcal{O}(Kn)$.
+In the case $K=n$ latter approach is preferred as it results in a runtime of $\mathcal{O}(n\log(n))$.
+However, choosing $K=n$ has not a real practical use case, as the ACF can always be cut off at small value, in the sense that $M \gtrsim K$.
+
+\subsection{Discrete Fourier and Cosine Transform}
+We define the Discrete Time Fourier Transform as
+\begin{equation}
+\mathrm{DTFT}[x]_n = \sum^{N-1}_{k=0} x_k \exp\left(-\frac{i2\pi kn}{N}\right)
+\end{equation}
+and its inverse by
+\begin{equation}
+\mathrm{DTFT}^{-1}[x]_n = \frac{1}{N}\sum^{N-1}_{k=0} x_k \exp\left(\frac{i2\pi kn}{N}\right).
+\end{equation}
+Sometimes, it can be handy to allow negative indices for a more ``natural'' representation.
+In the case that $n$ is even
+\begin{equation}
+\mathrm{DTFT}^{-1}[\hat{x}]_n = \frac{1}{N}\sum^{N/2+1}_{k=-N/2+2} \hat{x}_k \exp\left(\frac{i2\pi kn}{N}\right)
+\end{equation}
+and in the uneven case
+\begin{equation}
+\mathrm{DTFT}^{-1}[x]_n = \frac{1}{N}\sum^{(N-1)/2}_{k=-(N-1)/2} x_k \exp\left(\frac{i2\pi kn}{N}\right).
+\end{equation}
+The Discrete Cosine Transform of Type I is defined as
+\begin{equation}
+\mathrm{DCT}[x']_n = x'_0 + x'_{N'-1}(-1)^n + 2\sum_{k=0}^{N'-1} x'_k \cos \left(\frac{\pi k n}{N'-1}  \right).
+\end{equation}
+and its inverse is given by
+\begin{equation}
+\mathrm{DCT}^{-1}[x']_n = \frac{\mathrm{DCT}[x']_n}{2(N'-1)}
+\end{equation}
+The $\mathrm{DCT}$ is equivalent to a $\mathrm{DTFT}$ for a symmetric input but it is faster and uses less memory.
+More precisely, it can be shown that for $N=2(N'-1)$ and $x_i=x'_i$ for $i\in[0, N'-1]$ and $x_i=x'_{N-i}$ for $i\in[N', N-1]$ that
+\begin{equation}
+\mathrm{DTFT}^{-1}[x]_n = \mathrm{DCT}^{-1}[x']_n 
+\end{equation}
+where $n\in[0, N'-1]$.
+\subsection{From the continuous Fourier transform to the DCT}
+\begin{align}
+R(\tau) &= \int_{-\infty}^{\infty} \exp(-2\pi i\omega\tau) S(\omega) \d \omega \\
+&=2\int_{0}^{\infty} \cos(2\pi i\omega\tau) S(\omega) \d \omega
+\end{align}
+\begin{align}
+S(j\Delta_\omega) &= S_j\\
+R(j\Delta_\tau) &= R_j
+\end{align}
+As we only store a fixed number of samples, the period must be finite.
+This means, that a periodic continuation beyond the last sample ($S_{N-1}$) must be specified.
+In our case, even symmetry around $N-1$ is considered.
+As the first and last sample's bins shall be centered around $\omega=0$ and $\omega=(N-1)\Delta_\omega$ respectively, they have half width, so the integral becomes
+\begin{align}
+R_k = S_0\Delta_\omega + \cos({2\pi (N-1) k\Delta_\omega \Delta_\tau}) S_{N-1} + 2\sum_{j=1}^{j=N-2}\cos({2\pi j k \Delta_\omega \Delta_\tau}) S_j \Delta_\omega 
+\end{align}
+The maximum frequency (half bandwidth in our case) is $B = \Delta_\omega (N - 1)$.
+Now we can use the sampling theorem to find $\Delta_\tau = 1/(2B)$.
+\begin{align}
+R_k = \left(S_0 + (-1)^kS_{N-1} + 2\sum_{j=1}^{j=N-2}\cos \left(\frac{\pi j k}{N-1}  \right) S_j \right) \Delta_\omega
+\end{align}
+This is a type I DCT (Discrete Cosine Transform) according to scipy definition.
+
+\section{Calculation of codes}
+
 Due to technical limitations of the radar we have $\epsilon_i \in [-1, 1]$ and a naive brute force algorithm finds the following (shortest) codes for a given $N$ and $M$
@@
 		32&6&5&$-++-++++++++---++---+----++-+---$\\
+		32&8&3&$-+--++++++++-+---+--++++--+++---$\\
 		40&7&4&$-+--+++++++++-+++--+-+++----+-+++--++++-$\\
+		48&8&5&$--++++++++-+-+--+--+-++--+---+----++---++-+----+$\\
 		\bottomrule
@@
 Note that we have used that every code which is valid for $w$ is also valid for $-w$, because the value of the sum does not change if the code is shifted by $w$, due to the codes periodicity.
+
+\section{Possibility of using a Quantum SAT-Solver}
+
+The condition could be transformed to a boolean SAT problem, which could be solved by Grover's algorithm on a quantum computer.
+See \url{https://learn.qiskit.org/course/introduction/grovers-search-algorithm}.
+However, there are also different SAT-Solvers, which might pose a speedup compared to random guessing.
+There are also combinations of improved SAT-Solvers and quantum; investigate this.
+
 \end{document}

### 2022-03-15 doc/msp_code.tex
use j=0 for sums over codes
update doc

@@
 \section{Introduction}
-A binary phase radar code is presented which has optimal noise canceling properties, intrinsically measures the entire range at once (assuming that it is finite) and supports arbitrary radar duty cycles.
-\section{Mathematical description}
+A novel binary phase radar code is presented which has optimal noise canceling properties for the lag value estimator being considered.
+Furthermore, it is shown that the estimator is close to the Cramér–Rao bound.
+The code intrinsically measures the entire range at once, which must be finite.
+\section{Estimator and code requirement for zero bias}
 We assume that the radar code $\epsilon$ has length $L$ and is periodic $\epsilon_i = \epsilon_{i + L}$.
@@
 \begin{equation}
-\sum_{k=0}^{N-1} \epsilon_{i-k} V^{(k)}_i = m_i
+m_i = \sum_{k=0}^{N-1} \epsilon_{i-k} V^{(k)}_i
 \end{equation}
@@
 \begin{equation}
-\hat{R}^{(h)}_\Delta = \frac{1}{L}\sum^L_{j=1}\epsilon_{j + \Delta}m_{j + \Delta + h}^* \epsilon_j^*m_{j + h}.
+\hat{R}^{(h)}_\Delta = \frac{1}{L}\sum^{L-1}_{j=0}\epsilon_{j + \Delta}m_{j + \Delta + h}^* \epsilon_j^*m_{j + h}.
 \end{equation}
-for the autocorrelation function $R$ at altitude $h$ and lag $\Delta$ is considered.
+for the autocorrelation function $R$ at altitude $h$ and lag $\Delta > 0$ is introduced.
 In the following, it will be shown that this estimator is unbiased, if the code fulfills a certain condition.\\
@@
 \langle \hat{R}^{(h)}_\Delta \rangle
-=\frac{1}{L}\sum^L_{j=1} \epsilon_{j + \Delta}\epsilon_j^* \sum_{k=0}^{N-1} \epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k} \langle (V^{(k)}_{j + \Delta})^*V^{(k)}_j \rangle
+=\frac{1}{L}\sum^{L - 1}_{j=0} \epsilon_{j + \Delta}\epsilon_j^* \sum_{k=0}^{N-1} \epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k} \langle (V^{(k)}_{j + \Delta})^*V^{(k)}_j \rangle
 \end{equation}
@@
 = R^{(h)}_\Delta + \sum_{k=0,k\neq h}^{N-1}R^{(k)}_\Delta
-\left[ \frac{1}{L}\sum^L_{j=1}\epsilon_{j + \Delta}\epsilon_j^* \epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k}\right].
+\left[ \frac{1}{L}\sum^{L-1}_{j=0}\epsilon_{j + \Delta}\epsilon_j^* \epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k}\right].
 \end{equation}
@@
 \begin{equation}
-0 = \frac{1}{L}\sum^L_{j=1}\epsilon_{j}\epsilon_{j+w}^* \epsilon_{j+\Delta}^*\epsilon_{j + \Delta + w}.
+0 = \frac{1}{L}\sum^{L-1}_{j=0}\epsilon_{j}\epsilon_{j+w}^* \epsilon_{j+\Delta}^*\epsilon_{j + \Delta + w}.
 \label{eq:cond}
 \end{equation}
-In the next section, solutions of this equation are discussed.
+\subsection{Bias of a random code}
+For a random code, the condition is not exactly zero
+\begin{equation}
+r = \frac{1}{L}\sum^{L-1}_{j=0}\epsilon_{j}\epsilon_{j+w}^* \epsilon_{j+\Delta}^*\epsilon_{j + \Delta + w}.
+\end{equation}
+The variance is
+\begin{equation}
+\mathrm{Var}[r] = \frac{1}{L},
+\end{equation}
+which means that the result will be biased on average by
+\begin{equation}
+b^{(h)}_\Delta = \sum_{k=0,k\neq h}^{N-1}\frac{R^{(k)}_\Delta}{\sqrt{L}}
+\end{equation}
+
+\section{Optimizing the noise cancellation properties}
+The variance is calculated by
+\begin{equation}
+\langle |\hat{R}^{(h)}_\Delta|^2 \rangle = \frac{1}{L^2}\sum^{L-1}_{j_1=0}\sum^{L-1}_{j_2=0}
+\epsilon_{j_1} \epsilon_{j_1 + \Delta}
+\epsilon_{j_2} \epsilon_{j_2 + \Delta}
+\langle
+m_{j_1 + \Delta + h} m_{j_1 + h}^*
+m_{j_2 + \Delta + h}^* m_{j_2 + h}
+\rangle
+\end{equation}
+using Isserli's theorem on the four product of Gaussian random numbers
+\begin{equation}
+\mathrm{Var}[ \hat{R}^{(h)}_\Delta ] = \frac{1}{L^2}\sum^{L-1}_{j_1=0}\sum^{L-1}_{j_2=0}
+\epsilon_{j_1} \epsilon_{j_1 + \Delta}
+\epsilon_{j_2} \epsilon_{j_2 + \Delta}
+\langle m_{j_1 + \Delta + h} m_{j_2 + \Delta + h}^* \rangle
+\langle m_{j_2 + h} m_{j_1 + h}^* \rangle
+\end{equation}
+and using $\langle m_i m_j \rangle = 0$ yields the desired variance.
+Calculating the remaining expectation values
+\begin{equation}
+\langle m_{j_1}^*m_{j_2} \rangle = \sum_{k=0}^{N-1} \epsilon_{j_1-k} \epsilon_{j_2-k} R_{|j_1-j_2|}^{(k)}
+\end{equation}
+and substituting it into the previous expression result in
+\begin{equation}
+\mathrm{Var}[ \hat{R}^{(h)}_\Delta ] = \frac{1}{L^2}\sum^{L-1}_{j_1=0}\sum^{L-1}_{j_2=0}\sum_{k_1=0}^{N-1}\sum_{k_2=0}^{N-1}
+\hat{\epsilon}_{j_1}\hat{\epsilon}_{j_2} R_{|j_1-j_2|}^{(k_1)} R_{|j_1-j_2|}^{(k_2)}
+\end{equation}
+where
+\begin{equation}
+\hat{\epsilon}_j = \epsilon_j \epsilon_{j + \Delta} \epsilon_{j + h - k_2} \epsilon_{j + \Delta + h - k_1}
+\end{equation}
+was defined for brevity.
+By making use of the symmetry in $j_1 \leftrightarrow j_2$ it can be shown that
+\begin{equation}
+\mathrm{Var}[ \hat{R}^{(h)}_\Delta ] = \frac{1}{L}\left(\sum_{k_1=0}^{N-1} R_{0}^{(k_1)} \right)^2 +
+\frac{2}{L^2}\sum^{L-1}_{j_2=1}\sum^{L-1-j_2}_{j_1=0}\sum_{k_1=0}^{N-1}\sum_{k_2=0}^{N-1}
+\hat{\epsilon}_{j_1}\hat{\epsilon}_{j_1+j_2} R_{|j_2|}^{(k_1)} R_{|j_2|}^{(k_2)}.
+\end{equation}
+Now, the unknown product of $R$ variables does no longer depend $j_1$, but the codes are summed over $j_1$.
+For a random code of infinite length, the sum over $j_1$ will have zero expectation value.
+However, for a finite code the sum over $j_1$ can be negative, yielding additional noise suppression.
+The design of a code with maximal noise suppression appears to depend on the measurement results themselves.
+All codes which fulfill the bias free condition yield basically the same amount of noise suppression and appear like a random code to the second term.
+This gives effectively a standard deviation proportional to $N/L^{3/2}$ because $R$ drops exponentially with increasing $j_2$.
+So a long code might be better than a short periodic one.
 
@@
 The condition given by \eqref{eq:cond} is trivially fulfilled for pseudo random numbers if $L \rightarrow \infty$.
-However, the measurement would have no (definitive) time resolution in this case.
+However, the measurement would be biased and have no (definitive) time resolution in this case.
 With a brute-force computer search it can be shown that solutions do exist, when a finite $\Delta \in [1, M]$ is assumed, where $M$ is the total number of measurement points in the auto correlation function.
@@
 \begin{equation}
-s_i = \sum_{j=1}^{L}\gamma_{j, i}.
+s_i = \sum_{j=0}^{L-1}\gamma_{j, i}.
 \end{equation}
@@
 \begin{equation}
-s'_i s_i = \sum_{j'=1}^{L}\sum_{j=1}^{L}\gamma'_{j', i}\gamma_{j, i}.
+s'_i s_i = \sum_{j'=0}^{L-1}\sum_{j=0}^{L-1}\gamma'_{j', i}\gamma_{j, i}.
 \end{equation}
@@
 
+longest run in the beginning
+followed by an uneven number of runs
+511111
+5311
+
 \begin{equation}
@@
 \section{Modulating the code}
+\subsection{Modulation with fixed code}
 
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{code_diagram_modulated.pdf}
+	\caption{Range time diagram of the modulated version of the radar code with $S=3$.}
+	\label{fig:modulated}
+\end{figure}
+\begin{equation}
+m_{i,w} = \sum_{k=0}^{N-1} \epsilon_{i-k} \sum_{s=0}^{S-1} \gamma_{S-1-s} V^{(k, s + w)}_{i}
+\end{equation}
+\begin{equation}
+d_{i,w} = \sum^{S-1}_{s=0} \gamma_{s} m_{i, s + w}
+\end{equation}
+\begin{equation}
+d_{i,w} = \sum_{k=0}^{N-1}\epsilon_{i-k} \sum_{s_1=0}^{S-1} \sum^{S-1}_{s_2=0} \gamma_{s_2} \gamma_{S-1-s_1} V_i^{(k, s_1 + s_2 + w)}
+\end{equation}
+\begin{equation}
+d_{i,w} = \sum_{k=0}^{N-1}\epsilon_{i-k} \sum_{s_1=0}^{S-1} \sum^{S-1}_{s_2=0} \gamma_{s_1} \gamma_{s_2} V_i^{(k, S - 1 - s_1 + s_2 + w)}
+\end{equation}
+\begin{equation}
+d_{i,w} = \sum_{k=0}^{N-1}\epsilon_{i-k}\left[SV_i^{(k, S - 1 + w)}
++ \sum_{s_1=1}^{S-1} \sum^{S-1-s_1}_{s_2=0} \gamma_{s_2} \gamma_{s_1 + s_2} V_i^{(k, S - 1 + s_1 + w)}
++ \sum_{s_1=1}^{S-1} \sum^{S-1-s_1}_{s_2=0} \gamma_{s_2+s_1} \gamma_{s_2} V_i^{(k, S - 1 - s_1 + w)} \right]
+\end{equation}
+\begin{equation}
+A_{s_1} = \sum^{S-1-s_1}_{s_2=0} \gamma_{s_2+s_1} \gamma_{s_2}\text{ for }s_1\in[0, S-1]
+\end{equation}
+\begin{equation}
+d_{i,w} = \sum_{k=0}^{N-1}\epsilon_{i-k}\sum_{s=1-S}^{S-1} A_{|s|} V_i^{(k, S - 1 + s + w)}
+\end{equation}
+\begin{equation}
+\hat{R}^{(h, w)}_\Delta = \frac{1}{L}\sum^{L-1}_{j=0}
+\epsilon_{j + \Delta}d_{j + \Delta + h, w}^*
+\epsilon_jd_{j + h, w}.
+\end{equation}
+\begin{equation}
+\hat{R}^{(h, w)}_\Delta = \frac{1}{L}\sum^{L-1}_{j=0}
+\epsilon_{j + \Delta}
+\sum_{k_1=0}^{N-1}\epsilon_{j+\Delta+h-k_1}\sum_{s_1=1-S}^{S-1} A_{|s_1|} \left(V_{j+\Delta+h}^{(k_1, S - 1 + s_1 + w)}\right)^*
+\epsilon_j
+\sum_{k_2=0}^{N-1}\epsilon_{j+h-k_2}\sum_{s_2=1-S}^{S-1} A_{|s_2|} V_{j+h}^{(k_2, S - 1 + s_2 + w)}
+\end{equation}
+\begin{equation}
+\langle \hat{R}^{(h, w)}_\Delta \rangle = \frac{1}{L}\sum^{L-1}_{j=0}
+\epsilon_{j + \Delta}
+\sum_{k=0}^{N-1}\epsilon_{j+\Delta+h-k}\sum_{s_1=1-S}^{S-1} A_{|s_1|} 
+\epsilon_j
+\epsilon_{j+h-k}\sum_{s_2=1-S}^{S-1} A_{|s_2|} \left\langle \left(V_{j+\Delta+h}^{(k, S - 1 + s_1 + w)}\right)^* V_{j+h}^{(k, S - 1 + s_2 + w)} \right\rangle
+\end{equation}
+\begin{equation}
+\left\langle \left(V_{j+\Delta+h}^{(k, S - 1 + s_1 + w)}\right)^* V_{j+h}^{(k, S - 1 + s_2 + w)} \right\rangle =
+\delta_{s_1, s_2} R_\Delta^{(k, S-1+s_1+w)} +
+\delta_{s_1, s_2+1} R_\Delta^{(k, S-1+s_1+w + 0.5)}/2 +
+\delta_{s_1, s_2-1} R_\Delta^{(k, S-1+s_1+w - 0.5)}/2
+\end{equation}
+\begin{equation}
+\langle \hat{R}^{(h, w)}_\Delta \rangle =
+\sum_{s_1=1-S}^{S-1} A^2_{|s_1|}R_\Delta^{(h, S-1+s_1+w)}+
+\frac{1}{2}\sum_{s_1=1-S}^{S-2} A_{|s_1|}A_{|s_1+1|}R_\Delta^{(h, S-1+s_1+w+0.5)}+
+\frac{1}{2}\sum_{s_1=2-S}^{S-1} A_{|s_1|}A_{|s_1-1|}R_\Delta^{(h, S-1+s_1+w-0.5)}
+\end{equation}
+if $\gamma$ is a barker code we have $A_{|i|}A_{|i+1|}=0$
+\begin{equation}
+\langle \hat{R}^{(h, w)}_\Delta \rangle =
+\sum_{s_1=1-S}^{S-1} A^2_{|s_1|}R_\Delta^{(h, S-1+s_1+w)}
+\end{equation}
+so we find a biased estimator, where the signal is stronger by a factor
+\begin{equation}
+\frac{S^2}{S - 1}
+\end{equation}
+compared to the bias.
+one can also deconvolute, to find an exact result.
+\subsection{Modulation with variable code}
+\subsection{Hypothesis on code length}
 \section{Code with cyclic difference set for $\tau_i$}
-
-\section{Properties of the code}
-
 \section{Simulation}
@@
 \begin{equation}
-\mathrm{DTFT}^{-1}[x]_n = \frac{1}{N}\sum^{(N-1)/2}_{k=-(N-1)/2} x_k \exp\left(\frac{i2\pi kn}{N}\right).
+\mathrm{DTFT}^{-1}[\hat{x}]_n = \frac{1}{N}\sum^{(N-1)/2}_{k=-(N-1)/2} \hat{x}_k \exp\left(\frac{i2\pi kn}{N}\right).
 \end{equation}
@@
 
+\section{A lower bound for the variance}
+
+Assumptions made: monostatic radar, binary coded transmission, gaussian process
+A lower bound for the variance of any ACF estimation independent of the estimator is to be calculate, by means of the Cramér–Rao bound.
+What the radar measures (independent of the estimator) is
+\begin{equation}
+m_i=\sum_{k=0}^{N-1} \epsilon_{i-k} V^{(k)}_i.
+\end{equation}
+The parameters to be estimated are 
+\begin{equation}
+R^{(k)}_\Delta=\langle (V_{j+\Delta}^{(k)})^* V_j^{(k)} \rangle.
+\end{equation}
+The individual $m_i$ are random Gaussian distributed.
+The information is contained in the correlations.
+Define the probability density function $P = P(m_{1..n}, R^{(0..N-1)}_{1..M})$.
+We need to calculate $P$.
+the random variables $V^{(k)}_i$ are normally distributed with a correlation matrix of toeplitz type given by
+\begin{equation}
+\Sigma^{(k)}_{ij} = R_{i-j}^{(k)}
+\end{equation}
+then $m_i$ are Gaussian distributed according to
+\begin{equation}
+\Sigma_{ij} = \sum_{k=0}^{N-1} \epsilon_{i-k} \epsilon_{j-k} R_{|i-j|}^{(k)}.
+\end{equation}
+we note that the matrix is periodic with $\Sigma_{i,j} = \Sigma_{i+L,j+L}$
+where we imagine the matrix to be infinite in size as the auto correlation never drops to precisely to zero.
+The fisher information matrix for any zero mean Gaussian is
+\begin{equation}
+\mathcal{I}_{ij} = \frac{1}{2}\mathrm{tr}\left(\Sigma^{-1} \frac{\partial \Sigma}{\partial \theta_i} \Sigma^{-1} \frac{\partial \Sigma}{\partial \theta_j} \right)
+\end{equation}
+where each $\theta_i$ identifies exactly one parameter $\theta_i = R^{(k_i)}_{\Delta_i}$
+\begin{equation}
+\frac{\partial \Sigma_{ij}}{\partial \theta_p} = \epsilon_{i - k_p}\epsilon_{j - k_p}\delta_{|i-j|,\Delta_p}
+\end{equation}
+the fisher information matrix is
+\begin{equation}
+\mathcal{I}_{ij} = \frac{1}{2}\sum_{k_1, k_2, k_3, k_4}
+\Sigma^{-1}_{k_1, k_2}
+\epsilon_{k_2 - k_i}\epsilon_{k_3 - k_i}\delta_{|k_2-k_3|,\Delta_i}
+\Sigma^{-1}_{k_3, k_4}
+\epsilon_{k_4 - k_j}\epsilon_{k_1 - k_j}\delta_{|k_4-k_1|,\Delta_j}
+\end{equation}
+defining
+\begin{equation}
+\sigma_{\Delta_1, \Delta_2} =
+\epsilon_{k_2 - k_i}\epsilon_{k_2 + \Delta_1 - k_i}
+\epsilon_{k_1 - k_j}\epsilon_{k_1 + \Delta_2 - k_j}
+\Sigma^{-1}_{k_1, k_2}
+\Sigma^{-1}_{k_2 + \Delta_1, k_1 + \Delta_2}
+\end{equation}
+swapping $k_1 \leftrightarrow k_2$ and using symmetry of $\Sigma^{-1}$ it can be shown that
+\begin{equation}
+\sigma_{\Delta_1, \Delta_2} =
+\epsilon_{k_1 - k_i}\epsilon_{k_1 + \Delta_1 - k_i}
+\epsilon_{k_2 - k_j}\epsilon_{k_2 + \Delta_2 - k_j}
+\Sigma^{-1}_{k_1, k_2}
+\Sigma^{-1}_{k_1 + \Delta_1, k_2 + \Delta_2}
+\end{equation}
+using this definition results in
+\begin{equation}
+\mathcal{I}_{ij} = \frac{1}{2}\sum_{k_1, k_2}
+\left[\sigma_{\Delta_i, \Delta_j}+\sigma_{-\Delta_i, \Delta_j}+
+\sigma_{\Delta_i, -\Delta_j}+\sigma_{-\Delta_i, -\Delta_j}\right]
+\end{equation}
+for an infinite length random code with high $N$ the diagonal elements of $\Sigma$ grow proportional to $N$, while the off-diagonal elements have zero expectation value.
+They do have a standard deviation of $\sqrt{N}$ but for sufficient large $N$ a diagonal matrix is found:
+\begin{equation}
+\Sigma_{ij} = \delta_{ij} \sum_{k=0}^{N-1} R_{0}^{(k)}
+\end{equation}
+which has the trivial inverse
+\begin{equation}
+\Sigma^{-1}_{ij} = \delta_{ij} \left(\sum_{k=0}^{N-1} R_{0}^{(k)}\right)^{-1}
+\end{equation}
+when substituting this into $\sigma$ it can be seen that $\Delta_i=\Delta_j$ and $k_1=k_2$ must hold for $\sigma \neq 0$.
+\begin{equation}
+\sigma_{\Delta_1, \Delta_2} = \delta_{k_1 k_2}\delta_{\Delta_1\Delta_2}
+\epsilon_{k_1 - k_i}\epsilon_{k_1 + \Delta_1 - k_i}
+\epsilon_{k_2 - k_j}\epsilon_{k_2 + \Delta_2 - k_j}
+\left(\sum_{k=0}^{N-1} R_{0}^{(k)}\right)^{-2}
+\end{equation}
+the epsilons will square away for $k_i=k_j$ or special cases like $\Delta_1 = \Delta_2 = k_j, k_i=0$ but we are only interested in the main diagonal of the fisher matrix, so $k_i=k_j$.
+the fisher matrix is thus approximately given by
+\begin{equation}
+\mathcal{I}_{ij} = \delta_{ij} L \left(\sum_{k=0}^{N-1} R_{0}^{(k)}\right)^{-2}
+\end{equation}
+where we assumed $L$ measurements
+
+so the lower bound for the standard deviation is
+\begin{equation}
+\sigma \geq \frac{1}{\sqrt{L}}\sum_{k=0}^{N-1} R_{0}^{(k)}
+\end{equation}
+
 \section{Calculation of codes}

### 2022-03-15 solution_plot.py
current status of code search with plots

@@ -1,0 +1,136 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Mar 14 15:53:03 2022
+
+@author: frank
+"""
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+def check_code(c, k, h, Delta):
+    L = len(c)
+    cc = c*3
+    r = sum((cc[L + j + Delta]*cc[L + j]*
+             cc[L + j + Delta + h - k]*cc[L + j + h - k])
+            for j in range(L))
+    if r != 0:
+        print("code error:", k, h, Delta, r)
+
+
+def full_check(c, N, M):
+    for k in range(N):
+        for h in range(N):
+            if k != h:
+                for Delta in range(1, M+1):
+                    check_code(c, k, h, Delta)
+
+sols = []
+f = open("brute_code/solution_summary")
+L_vals = set()
+for line in f:
+    L = int(line.split(",")[1])
+    N = int(line.split(",")[2])
+    M = int(line.split(",")[3])
+    c = line.split("[")[1].split("]")[0].split(",")
+    code = [int(cc) for cc in c]
+    full_check(code, N, M-1)
+    assert len(code) == L
+    if N==8 and M==6:
+        print(code)
+    print(N, M, sum(code))
+    sols.append((N, M, code))
+max_N = max(t[0] for t in sols)
+max_M = max(t[1] for t in sols)
+res = np.zeros((max_M, max_N-1), dtype=np.int32)
+for N in range(2, max_N + 1):
+    for M in range(1, max_M + 1):
+        try:
+            L = len(next(t for t in sols if t[0] == N and t[1] == M)[2])
+        except StopIteration:
+            L = -1
+        res[M-1, N-2] = L
+        L_vals.add(L)
+res_c = np.zeros((max_M, max_N-1), dtype=np.int32)
+c = list(L_vals)
+c.sort()
+for N in range(2, max_N + 1):
+    for M in range(1, max_M + 1):
+        res_c[M-1, N-2] = c.index(res[M-1, N-2])
+cmap = plt.cm.get_cmap('tab10', len(L_vals))
+cmap.set_under((0.9, 0.9, 0.9))
+plt.imshow(res_c, cmap=cmap, origin="lower", interpolation="none")
+plt.xticks(range(max_N-1), range(2, max_N + 1))
+plt.yticks(range(max_M), range(1, max_M+1))
+for N in range(2, max_N+1):
[…]

### 2022-03-16 brute_code/code.c
anti cyclic imp

@@ -3,10 +3,27 @@
 
 using namespace std;
 
-static const unsigned int N = N_VAL, M = M_VAL, maxL = 60; // we assume M < N
+#ifndef N_VAL
+#error "define N_VAL"
+#endif
+#ifndef M_VAL
+#error "define M_VAL"
+#endif
+#ifndef MAX_L_VAL
+#define "define MAX_L_VAL"
+#endif
+static const unsigned int N = N_VAL, M = M_VAL, maxL = MAX_L_VAL; // we assume M < N
+#ifdef MIN_L_VAL
+static const unsigned int minL = MIN_L_VAL;
+#else
 static const unsigned int minL = (max(N, M + 1) + 1)/2*2;
+#endif
 
+#ifndef BIT_128
+typedef unsigned __int128 code_t;
+#else
 typedef uint64_t code_t;
+#endif
 
 /*
  * print code in +- format
@@ -74,19 +91,68 @@ __attribute__((optimize("unroll-loops"), always_inline)) inline void check(unsig
 }
 
 int main(){
+#ifdef IMPL_ENUM
+    cout << "running enumerate impl" << endl;
     // loop over bitvector length
     for(unsigned int L = minL; L <= maxL; L += 2){
         cout << "L: " << L << endl;
-        auto start = chrono::system_clock::now();
         // note that this parallelized loop acually checks only a quarter of the codes
         #pragma omp parallel for
         for(code_t c = code_t(1) << (L - 1); code_t(c) < (code_t(1) << L); c += 2){
             check(L, c);
         }
-        auto end = chrono::system_clock::now();
-        int elapsed = chrono::duration_cast<chrono::nanoseconds>(end - start).count();
-        if(elapsed > 0){
-            cout << "codes per sec " << 500*((code_t(1) << L) - (code_t(1) << (L - 1)))/elapsed << "e6" << endl;
+    }
+#else
+    typedef unsigned int uint;
+    typedef unsigned int run_len_t;
+
+    cout << "running anti-cyclic impl" << endl;
+    for(uint L = minL; L <= maxL; L += 2){
+        cout << "L: " << L << endl;
+        code_t alternating = 0;
+        for(uint i = 0; i < sizeof(code_t)*8; i += 2){
+            alternating += (code_t(1) << i);
+        }
+        #pragma omp parallel for num_threads(16)
+        for(uint leading = L - 1; leading >= 2; leading--){ // leading = 1 not supported
+            run_len_t sol[L - 2];
[…]

### 2022-03-16 cyclic_counter_prototypes.py
seperate prototypes from solution plotter

@@ -1,0 +1,278 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Mar 16 15:26:04 2022
+
+@author: frank
+"""
+
+import matplotlib.pyplot as plt
+
+def doit(leading, remaining, sol, sols):
+    if remaining == 0:
+        sols.append(sol)
+    else:
+        for digit in range(1, min(leading, remaining) + 1):
+            doit(leading, remaining - digit, sol + [digit], sols)
+
+x = []
+y = []
+for L in range(2, 25):
+    sols = []
+    for leading in range(1, L):
+        doit(leading, L - leading, [leading], sols)
+    x.append(L)
+    if L == 10:
+        f = sols
+        print(sols)
+    print(L, len(sols))
+    y.append(len(sols)/L**2/4)
+plt.plot(x, y)
+plt.grid()
+plt.yscale("log")
+plt.show()
+
+#%%
+
+sols_check = [(2, 1, 1, 1, 1, 1, 1, 1, 1, '1101010101'),
+ (2, 1, 1, 1, 1, 1, 1, 2, '1101010100'),
+ (2, 1, 1, 1, 1, 1, 2, 1, '1101010110'),
+ (2, 1, 1, 1, 1, 2, 1, 1, '1101010010'),
+ (2, 1, 1, 1, 1, 2, 2, '1101010011'),
+ (2, 1, 1, 1, 2, 1, 1, 1, '1101011010'),
+ (2, 1, 1, 1, 2, 1, 2, '1101011011'),
+ (2, 1, 1, 1, 2, 2, 1, '1101011001'),
+ (2, 1, 1, 2, 1, 1, 1, 1, '1101001010'),
+ (2, 1, 1, 2, 1, 1, 2, '1101001011'),
+ (2, 1, 1, 2, 1, 2, 1, '1101001001'),
+ (2, 1, 1, 2, 2, 1, 1, '1101001101'),
+ (2, 1, 1, 2, 2, 2, '1101001100'),
+ (2, 1, 2, 1, 1, 1, 1, 1, '1101101010'),
+ (2, 1, 2, 1, 1, 1, 2, '1101101011'),
+ (2, 1, 2, 1, 1, 2, 1, '1101101001'),
+ (2, 1, 2, 1, 2, 1, 1, '1101101101'),
+ (2, 1, 2, 1, 2, 2, '1101101100'),
+ (2, 1, 2, 2, 1, 1, 1, '1101100101'),
[…]

### 2022-03-16 solution_plot.py

@@ -39,7 +39,15 @@ for line in f:
     assert len(code) == L
     if N==8 and M==6:
         print(code)
-    print(N, M, sum(code))
+    cur = code[0]
+    res = [0]
+    for c in code[1:]:
+        if c == cur:
+            res[-1] += 1
+        else:
+            cur = c
+            res.append(1)
+    print(N, M, sum(code), max(res), len(res))
     sols.append((N, M, code))
 max_N = max(t[0] for t in sols)
 max_M = max(t[1] for t in sols)
@@ -74,63 +82,3 @@ plt.xlabel("N")
 plt.ylabel("M")
 #plt.savefig("code_length_overview.pdf")
 plt.show()
-
-
-#%%
-
-
-def doit(leading, remaining, sol, sols):
-    if remaining == 0:
-        #if len(sol) % 2 == 1:
-        sols.append(sol)
-    else:
-        for digit in range(1, min(leading, remaining) + 1):
-            doit(leading, remaining - digit, sol + [digit], sols)
-
-x = []
-y = []
-for L in range(2, 20):
-    sols = []
-    for leading in range(1, L):
-        doit(leading, L - leading, [leading], sols)
-    x.append(L)
-    if L == 10:
-        f = sols
-        print(sols)
-    print(L, len(sols))
-    y.append(len(sols)/L**2)
-plt.plot(x, y)
-
-#%%
-
-sols = []
-L = 10
-alternating = sum(1 << i for i in range(0, 64, 2))
-for leading in range(2, L):
-    c = L - leading
-    sol = [1]*(L - leading)
-    b = (1 << (leading - 1)) - 1
-    runs = 0
-    i = 0
-    while True:
-        if b % 2 == 0:
-            b = (b << (c + 1)) | (alternating >> (63 - c))
-        else:
-            b = (b << (c + 1)) | (alternating >> (62 - c))
-        runs += c
-        c = 0
-        print(f"{leading} {b:b} {[leading] + sol}")
-        sols.append([leading] + sol[:runs])
-        while runs > 0 and (sol[runs - 1] == leading or c == 0):
-            c += sol[runs - 1]
-            b = b >> sol[runs - 1]
-            sol[runs - 1] = 1
-            runs -= 1
-        if runs == 0:
-            break
-        sol[runs - 1] += 1
-        c -= 1
-        i += 1
-
-
-

### 2022-03-16 cyclic_counter_prototypes.py
add prototype for last leading bits brute force

@@ -15,18 +15,19 @@ def doit(leading, remaining, sol, sols):
         for digit in range(1, min(leading, remaining) + 1):
             doit(leading, remaining - digit, sol + [digit], sols)
 
-x = []
-y = []
-for L in range(2, 25):
+def solve_recursive(L):
     sols = []
     for leading in range(1, L):
         doit(leading, L - leading, [leading], sols)
+    return sols + [[L]]
+
+x = []
+y = []
+for L in range(2, 25):
+    sols = solve_recursive(L)
     x.append(L)
-    if L == 10:
-        f = sols
-        print(sols)
-    print(L, len(sols))
     y.append(len(sols)/L**2/4)
+    print(L, len(sols))
 plt.plot(x, y)
 plt.grid()
 plt.yscale("log")
@@ -34,153 +35,29 @@ plt.show()
 
 #%%
 
-sols_check = [(2, 1, 1, 1, 1, 1, 1, 1, 1, '1101010101'),
- (2, 1, 1, 1, 1, 1, 1, 2, '1101010100'),
- (2, 1, 1, 1, 1, 1, 2, 1, '1101010110'),
- (2, 1, 1, 1, 1, 2, 1, 1, '1101010010'),
- (2, 1, 1, 1, 1, 2, 2, '1101010011'),
- (2, 1, 1, 1, 2, 1, 1, 1, '1101011010'),
- (2, 1, 1, 1, 2, 1, 2, '1101011011'),
- (2, 1, 1, 1, 2, 2, 1, '1101011001'),
- (2, 1, 1, 2, 1, 1, 1, 1, '1101001010'),
- (2, 1, 1, 2, 1, 1, 2, '1101001011'),
- (2, 1, 1, 2, 1, 2, 1, '1101001001'),
- (2, 1, 1, 2, 2, 1, 1, '1101001101'),
- (2, 1, 1, 2, 2, 2, '1101001100'),
- (2, 1, 2, 1, 1, 1, 1, 1, '1101101010'),
- (2, 1, 2, 1, 1, 1, 2, '1101101011'),
- (2, 1, 2, 1, 1, 2, 1, '1101101001'),
- (2, 1, 2, 1, 2, 1, 1, '1101101101'),
- (2, 1, 2, 1, 2, 2, '1101101100'),
- (2, 1, 2, 2, 1, 1, 1, '1101100101'),
- (2, 1, 2, 2, 1, 2, '1101100100'),
[…]

### 2022-03-16 solution_plot.py
improve formatting

@@ -47,7 +47,7 @@ for line in f:
         else:
             cur = c
             res.append(1)
-    print(N, M, sum(code), max(res), len(res))
+    print(f"N: {N:2d}, M: {M:2d} L: {L:2d}, runs: {len(res):2d}")
     sols.append((N, M, code))
 max_N = max(t[0] for t in sols)
 max_M = max(t[1] for t in sols)

### 2022-03-16 brute_code/code.c
optimize with __builtin_expect

@@ -134,15 +134,15 @@ int main(){
                 if((runs&1) == 0){
                     check(L, b);
                 }
-                if(runs == 0){
+                if(__builtin_expect(runs == 0, 0)){
                     break;
                 }
                 c = sol[runs];
                 sol[runs] = 1;
                 code_t prev = sol[runs - 1];
-                while(prev == leading){
+                while(__builtin_expect(prev == leading, 0)){
                     runs--;
-                    if(runs == 0){
+                    if(__builtin_expect(runs == 0, 0)){
                         goto out;
                     }
                     c += prev;

### 2022-03-16 cyclic_counter_prototypes.py
only enumerate solutions with an even number of runs

@@ -45,7 +45,9 @@ for sol in sols:
             res += "1"*c
         else:
             res += "0"*c
-    sols_check.append(res)
+    if res[-1] == "0":
+        sols_check.append(res)
+assert len(sols_check) == len(set(sols_check))
 
 #%%
 
@@ -53,7 +55,7 @@ sols = []
 L = 10
 alternating = sum(1 << i for i in range(0, 64, 2))
 sol = [1]*(L - 2)
-for leading in range(1, L//2):
+for leading in range(2, L//2):
     L_algo = L - leading # the remaining leading bits are brute-forced
     c = L_algo - leading
     b = (1 << (leading - 1)) - 1
@@ -67,13 +69,19 @@ for leading in range(1, L//2):
         runs += c - 2
         c = sol[runs]
         start = 1 << (c - 1)
-        end = (1 << leading) - 1
-        if (runs&1) == 1:
-            end -= start
+        end = (1 << leading) - 2
+        if (runs&1) == 0:
+            start = 1 << (c - 1)
+            if start == 1:
+                start += 1
+            end = (1 << leading) - 2
+        else:
             start = 0
+            end = (1 << leading) - 1 - (1 << (c - 1))
+        print(f"{start:b} {end:b}")
         start |= (b << leading)
         end |= (b << leading)
-        for lastbits in range(start, end + 1):
+        for lastbits in range(start, end + 1, 2):
             print(f"{lastbits:02b} {[leading] + sol[:runs+1]}")
             sols.append(tuple([leading] + sol[:runs+1] + [f"{lastbits:b}"]))
         if runs == 0:
@@ -93,10 +101,10 @@ for leading in range(1, L//2):
             break
         sol[runs - 1] = prev + 1
 start = ((1 << L//2) - 1) << L//2
-end = ((1 << L) - 1)
-for brute_bits in range(start, end + 1):
+end = (1 << L) - 2
+for brute_bits in range(start, end + 1, 2):
     sols.append(("brute", f"{brute_bits:02b}"))
-
+sols.append(("last", f"{(alternating >> (63 - L)):b}"))
 assert set(sols_check) == set(t[-1] for t in sols)
 
 

### 2022-03-16 brute_code/code.c
add version with inner loop

@@ -97,7 +97,7 @@ int main(){
     for(unsigned int L = minL; L <= maxL; L += 2){
         cout << "L: " << L << endl;
         // note that this parallelized loop acually checks only a quarter of the codes
-        #pragma omp parallel for
+        //#pragma omp parallel for schedule(static, 4096)
         for(code_t c = code_t(1) << (L - 1); code_t(c) < (code_t(1) << L); c += 2){
             check(L, c);
         }
@@ -106,38 +106,56 @@ int main(){
     typedef unsigned int uint;
     typedef unsigned int run_len_t;
 
+    // this algorithm checks all cyclic-unique combinations which start with 1 except 101010101...
+    // note that by convention the constant sequence is not anti-cyclic
     cout << "running anti-cyclic impl" << endl;
+#ifdef COUNT
+    uint64_t counter = 0;
+#endif
+    code_t end, b, code, alternating = 0;
+    for(uint i = 0; i < sizeof(code_t)*8; i += 2){
+        alternating += (code_t(1) << i);
+    }
     for(uint L = minL; L <= maxL; L += 2){
         cout << "L: " << L << endl;
-        code_t alternating = 0;
-        for(uint i = 0; i < sizeof(code_t)*8; i += 2){
-            alternating += (code_t(1) << i);
-        }
-        #pragma omp parallel for num_threads(16)
-        for(uint leading = L - 1; leading >= 2; leading--){ // leading = 1 not supported
-            run_len_t sol[L - 2];
-            uint c = L - leading;
-            code_t b = (code_t(1) << (leading - 1)) - 1; // start with leading sequence one bit shorter
-            for(uint i = 0; i < L - leading; i++){
+        for(uint leading = L/2 - 1; leading >= 2; leading--){
+            uint L_algo = L - leading;
+            run_len_t sol[L_algo - 2];
+            uint c = L_algo - leading;
+            b = (code_t(1) << (leading - 1)) - 1; // start with leading sequence one bit shorter
+            for(uint i = 0; i < L_algo - leading; i++){
                 sol[i] = 1;
             }
             uint runs = 0;
             b = b << (c + 1);
             c += 1;
-            #pragma omp critical 
-            {
-                cout << "leading " << leading << endl;
-            }
+            cout << "leading " << leading << endl;
             while(1){
                 b = ((b >> c) << c) | (alternating >> (sizeof(code_t)*8 - 1 - c + (runs&1)));
                 runs += c - 2; // all added runs should have length 1
+                c = sol[runs];
[…]

### 2022-03-16 cyclic_counter_prototypes.py

@@ -21,16 +21,30 @@ def solve_recursive(L):
         doit(leading, L - leading, [leading], sols)
     return sols + [[L]]
 
-x = []
-y = []
-for L in range(2, 25):
+x, y, y_comb = [], [], []
+for L in range(3, 25):
     sols = solve_recursive(L)
+    if L < 10:
+        print(sols)
     x.append(L)
-    y.append(len(sols)/L**2/4)
+    y.append(2**(L - 2)/(len(sols)/2 - 1))
+    y_comb.append(len(sols)/2 - 1)
     print(L, len(sols))
-plt.plot(x, y)
+x.append(34)
+y.append(2**(34 - 2)/358728827)
+x.append(36)
+y.append(2**(36 - 2)/1356530952)
+
+#%%
+
+# no parallel 157 (static schedule 50, def schedule 44, 1024 schedule 36, 4096: 48)
+
+plt.scatter([36, 34, 32], [50.76/10, 7.81/1.95, 0.804/0.77], label="notebook, 64 bit, single core, exhaustive, inner exact loop")
+plt.plot(x, y, label="max speedup", c="black")
 plt.grid()
-plt.yscale("log")
+plt.legend()
+plt.title("speedup")
+plt.grid()
 plt.show()
 
 #%%
@@ -54,9 +68,9 @@ assert len(sols_check) == len(set(sols_check))
 sols = []
 L = 10
 alternating = sum(1 << i for i in range(0, 64, 2))
-sol = [1]*(L - 2)
-for leading in range(2, L//2):
+for leading in list(range(2, L//2))[::-1]:
     L_algo = L - leading # the remaining leading bits are brute-forced
+    sol = [None]*(L_algo - 2)
     c = L_algo - leading
     b = (1 << (leading - 1)) - 1
     for i in range(L_algo - leading):
@@ -68,8 +82,6 @@ for leading in range(2, L//2):
         b = ((b >> c) << c) | (alternating >> (63 - c + (runs&1)))
         runs += c - 2
         c = sol[runs]
-        start = 1 << (c - 1)
-        end = (1 << leading) - 2
         if (runs&1) == 0:
             start = 1 << (c - 1)
             if start == 1:
@@ -78,7 +90,7 @@ for leading in range(2, L//2):
         else:
             start = 0
             end = (1 << leading) - 1 - (1 << (c - 1))
-        print(f"{start:b} {end:b}")
+        print(f"{b:b} {start:b} {end:b}")
[…]

### 2022-03-17 brute_code/code.c
add stacked-loop impl

@@ -30,10 +30,10 @@ typedef uint64_t code_t;
  */
 void print(unsigned int L, code_t c){
     for(unsigned int i = 0; i < L; i++){
-        if((c >> (L - i - 1)) & 1){
-            cout << "-";
+        if((c >> (L - i - 1))&1){
+            cout << "1";
         }else{
-            cout << "+";
+            cout << "0";
         }
     }
     cout << endl;
@@ -97,12 +97,12 @@ int main(){
     for(unsigned int L = minL; L <= maxL; L += 2){
         cout << "L: " << L << endl;
         // note that this parallelized loop acually checks only a quarter of the codes
-        //#pragma omp parallel for schedule(static, 4096)
+        #pragma omp parallel for num_threads(6) schedule(static)
         for(code_t c = code_t(1) << (L - 1); code_t(c) < (code_t(1) << L); c += 2){
             check(L, c);
         }
     }
-#else
+#elif IMPL_RUN_STACK
     typedef unsigned int uint;
     typedef unsigned int run_len_t;
 
@@ -149,7 +149,6 @@ int main(){
 #endif
                 code |= (b << leading);
                 end |= (b << leading);
-//                #pragma omp parallel for schedule(static)
                 for(code_t c = code; c <= end; c += 2){
                     check(L, c);
                 }
@@ -177,7 +176,7 @@ int main(){
 #ifdef COUNT
         counter += ((end - code) >> 1) + 1;
 #endif
-#pragma omp parallel for
+        //#pragma omp parallel for
         for(code_t c = code; c <= end; c += 2){
             check(L, c);
         }
@@ -185,5 +184,91 @@ int main(){
         cout << "counter: " << counter << endl;
 #endif
     }
+#else
+    typedef unsigned int uint;
+    typedef unsigned int sub_code_t;
+
+    // this algorithm checks all cyclic-unique combinations which start with 1 except 101010101...
+    // note that by convention the constant sequence is not anti-cyclic
+    cout << "running stacked loop impl" << endl;
+#ifdef COUNT
+    uint64_t counter = 0;
+#endif
+    code_t code, end_code, prev_code;
+    for(uint L = minL; L <= maxL; L += 2){
+        cout << "L: " << L << endl;
+        for(uint leading = L/2 - 1; leading >= 2; leading--){
+            cout << "leading " << leading << endl;
+            uint remaining = L - leading - 1;
+            uint seqs = remaining/leading;
[…]

### 2022-03-17 brute_code/code.c
add parallel version

@@ -1,7 +1,10 @@
 #include <iostream>
 #include <chrono>
+#include <omp.h>
 
 using namespace std;
+
+#define NUM_THREADS 6
 
 #ifndef N_VAL
 #error "define N_VAL"
@@ -91,13 +94,14 @@ __attribute__((optimize("unroll-loops"), always_inline)) inline void check(unsig
 }
 
 int main(){
+    omp_set_num_threads(NUM_THREADS);
 #ifdef IMPL_ENUM
     cout << "running enumerate impl" << endl;
     // loop over bitvector length
     for(unsigned int L = minL; L <= maxL; L += 2){
         cout << "L: " << L << endl;
         // note that this parallelized loop acually checks only a quarter of the codes
-        #pragma omp parallel for num_threads(6) schedule(static)
+        #pragma omp parallel for
         for(code_t c = code_t(1) << (L - 1); code_t(c) < (code_t(1) << L); c += 2){
             check(L, c);
         }
@@ -194,79 +198,107 @@ int main(){
 #ifdef COUNT
     uint64_t counter = 0;
 #endif
-    code_t code, end_code, prev_code;
     for(uint L = minL; L <= maxL; L += 2){
         cout << "L: " << L << endl;
-        for(uint leading = L/2 - 1; leading >= 2; leading--){
-            cout << "leading " << leading << endl;
-            uint remaining = L - leading - 1;
-            uint seqs = remaining/leading;
-            uint buffer_seq_len = remaining%leading;
-            sub_code_t mask = (sub_code_t(1) << leading) - 1;
-            code = mask;
-            code = code << (1 + buffer_seq_len); // we start with leading sequence followed by the zero and the buffer seq
-            sub_code_t buffer_end_exclusive = 1 << buffer_seq_len;
-            for(sub_code_t buffer_seq = 0; buffer_seq < buffer_end_exclusive; buffer_seq++){
-                uint start = 0;
-                if(buffer_seq == 0){
-                    start = sub_code_t(1) << buffer_seq_len; 
-                }else if((buffer_seq&1) == 0){
-                    start = sub_code_t(1) << (__builtin_ctz(buffer_seq) - 1);
-                }
-                code = ((((code >> buffer_seq_len) << buffer_seq_len) | buffer_seq) << leading) | start;
-                uint cur_pos = leading*(seqs - 1);
-                uint goup = 0;
-                do{
-                    prev_code = code >> leading;
-                    sub_code_t end = mask;
[…]

### 2022-03-17 brute_code/code.c
fix bug in makro

@@ -22,7 +22,7 @@ static const unsigned int minL = MIN_L_VAL;
 static const unsigned int minL = (max(N, M + 1) + 1)/2*2;
 #endif
 
-#ifndef BIT_128
+#ifdef BIT_128
 typedef unsigned __int128 code_t;
 #else
 typedef uint64_t code_t;

### 2022-03-17 cyclic_counter_prototypes.py
add plots

@@ -33,21 +33,43 @@ for L in range(3, 25):
 x.append(34)
 y.append(2**(34 - 2)/358728827)
 x.append(36)
+#                    1687422392
 y.append(2**(36 - 2)/1356530952)
 
 #%%
 
-# no parallel 157 (static schedule 50, def schedule 44, 1024 schedule 36, 4096: 48)
-
-plt.scatter([36, 34, 32], [50.76/10, 7.81/1.95, 0.804/0.77], label="notebook, 64 bit, single core, exhaustive, inner exact loop")
-plt.plot(x, y, label="max speedup", c="black")
+# runs with N=6, M=8
+plt.scatter([32, 34, 36], [6.5/0.612, 20.45/1.91, 105/9], label="single core, exhaustive")
+plt.scatter([32, 34, 36], [1.194/0.134, 3.417/0.368, 18.34/1.668], label="multi core, exhaustive")
+plt.plot(x, y, label="theoretical maximum", c="black")
 plt.grid()
 plt.legend()
-plt.title("speedup")
+plt.title("speedup on server, 128bit")
 plt.grid()
 plt.show()
 
 #%%
+
+# factor three penalty for using 128bit vector instead of 64bit
+plt.scatter([32, 34, 36], [1.194, 3.417, 18.34], label="exhaustive, 128bit, enum")
+plt.scatter([32, 34, 36], [0.134, 0.368, 1.668], label="exhaustive, 128bit, loops")
+plt.scatter([48], [8*60 + 55], label="N=8, M=6, 128bit, enum")
+plt.scatter([48], [5*60 + 8.4], label="N=8, M=6, 128bit, loops")
+plt.scatter([48], [1*60 + 44], label="N=8, M=6, 64bit, loops")
+plt.scatter([40], [0.189], label="N=7, M=5, 128bit, enum")
+plt.scatter([40], [0.514], label="N=6, M=8, 128bit, loops")
+plt.yscale("log")
+plt.axhline(3600*24, label="1 day")
+plt.grid()
+plt.xlim(31, 60)
+plt.ylim(0.1, 10e5)
+plt.title("runtime, multi-core")
+plt.legend(loc="upper left")
+plt.show()
+
+
+#%%
+
 
 L = 10
 sols = solve_recursive(L)
@@ -118,9 +140,6 @@ for brute_bits in range(start, end + 1, 2):
     sols.append(("brute", f"{brute_bits:02b}"))
[…]

### 2022-03-17 cyclic_counter_prototypes.py
factor out plotter

@@ -6,73 +6,10 @@ Created on Wed Mar 16 15:26:04 2022
 @author: frank
 """
 
-import matplotlib.pyplot as plt
-
-def doit(leading, remaining, sol, sols):
-    if remaining == 0:
-        sols.append(sol)
-    else:
-        for digit in range(1, min(leading, remaining) + 1):
-            doit(leading, remaining - digit, sol + [digit], sols)
-
-def solve_recursive(L):
-    sols = []
-    for leading in range(1, L):
-        doit(leading, L - leading, [leading], sols)
-    return sols + [[L]]
-
-x, y, y_comb = [], [], []
-for L in range(3, 25):
-    sols = solve_recursive(L)
-    if L < 10:
-        print(sols)
-    x.append(L)
-    y.append(2**(L - 2)/(len(sols)/2 - 1))
-    y_comb.append(len(sols)/2 - 1)
-    print(L, len(sols))
-x.append(34)
-y.append(2**(34 - 2)/358728827)
-x.append(36)
-#                    1687422392
-y.append(2**(36 - 2)/1356530952)
-
-#%%
-
-# runs with N=6, M=8
-plt.scatter([32, 34, 36], [6.5/0.612, 20.45/1.91, 105/9], label="single core, exhaustive")
-plt.scatter([32, 34, 36], [1.194/0.134, 3.417/0.368, 18.34/1.668], label="multi core, exhaustive")
-plt.plot(x, y, label="theoretical maximum", c="black")
-plt.grid()
-plt.legend()
-plt.title("speedup on server, 128bit")
-plt.grid()
-plt.show()
-
-#%%
-
-# factor three penalty for using 128bit vector instead of 64bit
-plt.scatter([32, 34, 36], [1.194, 3.417, 18.34], label="exhaustive, 128bit, enum")
-plt.scatter([32, 34, 36], [0.134, 0.368, 1.668], label="exhaustive, 128bit, loops")
-plt.scatter([48], [8*60 + 55], label="N=8, M=6, 128bit, enum")
-plt.scatter([48], [5*60 + 8.4], label="N=8, M=6, 128bit, loops")
-plt.scatter([48], [1*60 + 44], label="N=8, M=6, 64bit, loops")
-plt.scatter([40], [0.189], label="N=7, M=5, 128bit, enum")
-plt.scatter([40], [0.514], label="N=6, M=8, 128bit, loops")
-plt.yscale("log")
[…]

### 2022-03-17 perf_plotter.py

@@ -1,0 +1,51 @@
+# -*- coding: utf-8 -*-
+
+import matplotlib.pyplot as plt
+import recursive_counter
+
+x, y, y_comb = [], [], []
+for L in range(3, 25):
+    sols = recursive_counter.solve_recursive(L)
+    if L < 10:
+        print(sols)
+    x.append(L)
+    y.append(2**(L - 2)/(len(sols)/2 - 1))
+    y_comb.append(len(sols)/2 - 1)
+    print(L, len(sols))
+x.append(34)
+y.append(2**(34 - 2)/358728827)
+x.append(36)
+y.append(2**(36 - 2)/1356530952)
+
+#%%
+
+# runs with N=6, M=8
+plt.scatter([32, 34, 36], [6.5/0.612, 20.45/1.91, 105/9], label="single core, exhaustive")
+plt.scatter([32, 34, 36], [1.194/0.134, 3.417/0.368, 18.34/1.668], label="multi core, exhaustive")
+plt.plot(x, y, label="theoretical maximum", c="black")
+plt.grid()
+plt.legend()
+plt.title("speedup on server (enum vs. loops impl), 128bit")
+plt.grid()
+plt.savefig("speedup.pdf")
+plt.show()
+
+#%%
+
+# factor three penalty for using 128bit vector instead of 64bit
+plt.scatter([32, 34, 36], [1.194, 3.417, 18.34], label="exhaustive, 128bit, enum", marker="^")
+plt.scatter([32, 34, 36], [0.134, 0.368, 1.668], label="exhaustive, 128bit, loops")
+plt.scatter([48], [8*60 + 55], label="N=8, M=6, 128bit, enum", marker="^")
+plt.scatter([48], [5*60 + 8.4], label="N=8, M=6, 128bit, loops")
+plt.scatter([48], [1*60 + 44], label="N=8, M=6, 64bit, loops")
+plt.scatter([40], [0.189], label="N=7, M=5, 128bit, enum", marker="^")
+plt.scatter([40], [0.514], label="N=6, M=8, 128bit, loops")
+plt.yscale("log")
+plt.axhline(3600*24, label="1 day")
+plt.grid()
+plt.xlim(31, 60)
+plt.ylim(0.1, 10e5)
+plt.title("runtime, multi-core")
+plt.legend(loc="upper left")
+plt.savefig("perf_plot.pdf")
+plt.show()

### 2022-03-17 recursive_counter.py

@@ -1,0 +1,20 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Mar 17 19:44:23 2022
+
+@author: frank
+"""
+
+def doit(leading, remaining, sol, sols):
+    if remaining == 0:
+        sols.append(sol)
+    else:
+        for digit in range(1, min(leading, remaining) + 1):
+            doit(leading, remaining - digit, sol + [digit], sols)
+
+def solve_recursive(L):
+    sols = []
+    for leading in range(1, L):
+        doit(leading, L - leading, [leading], sols)
+    return sols + [[L]]

### 2022-05-11 solution_plot.py
add new codes and change color scheme

@@ -51,6 +51,7 @@ for line in f:
 
 sols.append((9, 5, [], 58))
 sols.append((10, 4, [], 56))
+sols.append((25, 1, [], 56))
 
 max_N = max(t[0] for t in sols)
 max_M = max(t[1] for t in sols)
@@ -71,7 +72,7 @@ c.sort()
 for N in range(2, max_N + 1):
     for M in range(1, max_M + 1):
         res_c[M-1, N-2] = c.index(res[M-1, N-2])
-cmap = plt.cm.get_cmap('tab10', len(L_vals))
+cmap = plt.cm.get_cmap('Set3', len(L_vals))
 cmap.set_under((0.9, 0.9, 0.9))
 plt.imshow(res_c, cmap=cmap, origin="lower", interpolation="none")
 plt.xticks(range(max_N-1), range(2, max_N + 1))

### 2022-05-11 doc/msp_code.tex
update doc

@@
 \DeclareMathOperator{\sgn}{sgn}
+\DeclareMathOperator{\Cov}{Cov}
+\renewcommand{\Re}{\mathrm{Re}}
 \renewcommand{\d}[1]{\ensuremath{\operatorname{d}\!{#1}}}
@@
 \end{equation}
+However, one would use deconvolution (lag profile inversion) for a random code, this would remove the bias.
 
@@
 \begin{equation}
-\mathrm{Var}[ \hat{R}^{(h)}_\Delta ] = \frac{1}{L^2}\sum^{L-1}_{j_1=0}\sum^{L-1}_{j_2=0}\sum_{k_1=0}^{N-1}\sum_{k_2=0}^{N-1}
+\mathrm{Var}[ \hat{R}^{(h)}_\Delta ] =
+\frac{1}{L^2}\sum^{L-1}_{j_1=0}\sum^{L-1}_{j_2=0}\sum_{k_1=0}^{N-1}\sum_{k_2=0}^{N-1}
 \hat{\epsilon}_{j_1}\hat{\epsilon}_{j_2} R_{|j_1-j_2|}^{(k_1)} R_{|j_1-j_2|}^{(k_2)}
@@
 So a long code might be better than a short periodic one.
+
+\section{Covariance with correct calculation of real part - also use this for variance}
+
+\begin{equation}
+\left \langle
+\Re\left(\hat{R}^{(h)}_{\Delta_1}\right)
+\Re\left(\hat{R}^{(h)}_{\Delta_2}\right)
+\right \rangle =
+\frac{1}{L^2}\sum^{L-1}_{j_1=0}\sum^{L-1}_{j_2=0}
+\epsilon_{j_1} \epsilon_{j_1 + \Delta_1}
+\epsilon_{j_2} \epsilon_{j_2 + \Delta_2}
+\left\langle
+\Re\left(m_{j_1 + \Delta_1 + h} m_{j_1 + h}^*\right)
+\Re\left(m_{j_2 + \Delta_2 + h}^* m_{j_2 + h}\right)
+\right\rangle
+\end{equation}
+
+\begin{equation*}
+\begin{split}
+2\left\langle
+\Re\left(m_{j_1 + \Delta_1 + h}m_{j_1 + h}^*\right)
+\Re\left(m_{j_2 + \Delta_2 + h}^* m_{j_2 + h}\right)
+\right\rangle
+= \: &
+\Re\left(\left\langle m_{j_1 + \Delta_1 + h} m_{j_1 + h}^* m_{j_2 + \Delta_2 + h}^* m_{j_2 + h}\right\rangle\right)+ \\&
+\Re\left(\left\langle m_{j_1 + \Delta_1 + h}^* m_{j_1 + h} m_{j_2 + \Delta_2 + h}^* m_{j_2 + h}\right\rangle\right)
+\end{split}
+\end{equation*}
+
+plugged into the previous expression this gives
+
+\begin{equation*}
+\begin{split}
+\left \langle
+\Re\left(\hat{R}^{(h)}_{\Delta_1}\right)
+\Re\left(\hat{R}^{(h)}_{\Delta_2}\right)
+\right \rangle = \: &
+\frac{1}{2}\Re\left(\left\langle\hat{R}^{(h)}_{\Delta_1}\right\rangle^* \left\langle\hat{R}^{(h)}_{\Delta_2} \right\rangle\right)+
+\frac{1}{2}\Re\left(\left\langle\hat{R}^{(h)}_{\Delta_1}\right\rangle \left\langle\hat{R}^{(h)}_{\Delta_2} \right\rangle\right)+ \\&
+\frac{1}{2L^2}\sum^{L-1}_{j_1=0}\sum^{L-1}_{j_2=0}
+\epsilon_{j_1} \epsilon_{j_1 + \Delta_1}
+\epsilon_{j_2} \epsilon_{j_2 + \Delta_2}
+A
+\end{split}
+\end{equation*}
+
+\begin{equation*}
+A = \Re\left(\left
+\langle m_{j_2 + \Delta_2 + h}^* m_{j_1 + \Delta_1 + h} \rangle
+\langle m_{j_1 + h}^* m_{j_2 + h} \rangle
+\right\rangle\right) +
+\Re\left(\left
+\langle m_{j_1 + \Delta_1 + h}^* m_{j_2 + h} \rangle
+\langle m_{j_2 + \Delta_2 + h}^* m_{j_1 + h} \rangle
+\right\rangle\right)
+\end{equation*}
+
+\begin{equation*}
+\Cov\left[
+\Re\left( \hat{R}^{(h)}_{\Delta_1} \right),
+\Re\left( \hat{R}^{(h)}_{\Delta_2} \right)
+\right] = \frac{1}{2L^2}\sum^{L-1}_{j_1=0}\sum^{L-1}_{j_2=0}
+\epsilon_{j_1} \epsilon_{j_1 + \Delta_1}
+\epsilon_{j_2} \epsilon_{j_2 + \Delta_2}
+A
+\end{equation*}
+
+\begin{equation*}
+\hat{\epsilon}_{j, \Delta, l_1, l_2} = \epsilon_j \epsilon_{j + \Delta} \epsilon_{j + h - l_2} \epsilon_{j + \Delta + h - l_1}
+\end{equation*}
+
+\begin{equation*}
+\Cov\left[
+\Re\left( \hat{R}^{(h)}_{\Delta_1} \right),
+\Re\left( \hat{R}^{(h)}_{\Delta_2} \right)
+\right] = \frac{1}{2L^2}
+\sum^{L-1}_{j_1=0}\sum^{L-1}_{j_2=0}
+\sum_{k_1=0}^{N-1}\sum_{k_2=0}^{N-1}\left(A+B\right)
+\end{equation*}
+
+\begin{align}
+A &= \hat{\epsilon}_{j_1, \Delta_1, k_1, k_2}\hat{\epsilon}_{j_2, \Delta_2, k_1, k_2}
+\Re\left( R^{(k_1)}_{j_2 - j_1 + \Delta_2 - \Delta_1}R^{(k_2)}_{j_2 - j_1} \right)\\
+B &= \hat{\epsilon}_{j_1, \Delta_1, k_1, k_2}\hat{\epsilon}_{j_2, \Delta_2, k_2, k_1}
+\Re\left( R^{(k_1)}_{j_1 - j_2 + \Delta_1}R^{(k_2)}_{j_2 - j_1 + \Delta_2} \right)
+\end{align}
 
@@
 
+5 3 2 5 4
+
+for s >= 0:
+5: -min(s, 3)
+3: -min(s, 2)
+2: -min(s, 2)
+4: -min(s, 4) + min(s - 5, 0)
+
 \begin{equation}
@@
 \section{Modulating the code}
-\subsection{Modulation with fixed code}
-
+\subsection{Modulation with fixed code, match filter on pulse, ignoring voltage changes}
+In the following it is considered that the recieved modulated voltage is demodulated first with an inverse filter and then correlated.
+This leads to a nice analytical expression, but only if the voltage during one pulse is condidered constant, which is wrong...
 \begin{figure}
@@
 \end{equation}
+\begin{equation}
+w \in [0, K - S]
+\end{equation}
+Where $K$ is the number of bits received.
 \begin{equation}
@@
 \epsilon_{j + \Delta}d_{j + \Delta + h, w}^*
-\epsilon_jd_{j + h, w}.
+\epsilon_jd_{j + h, w}
 \end{equation}
@@
 \end{equation}
-if $\gamma$ is a barker code we have $A_{|i|}A_{|i+1|}=0$
+if $\gamma$ is a Barker code we have $A_{|i|}A_{|i+1|}=0$
 \begin{equation}
@@
 one can also deconvolute, to find an exact result.
-\subsection{Modulation with variable code}
-\subsection{Hypothesis on code length}
+
+\subsection{Modulation with fixed code, match filter on pulse}
+\begin{equation}
+m_{i,w} = \sum_{k=0}^{N-1} \epsilon_{i-k} \sum_{s=0}^{S-1} \gamma_{S-1-s} V^{(k, s + w)}_{i, w}
+\end{equation}
+\begin{equation}
+d_{i,w} = \sum^{S-1}_{s=0} \gamma_{s} m_{i, s + w}
+\end{equation}
+\begin{equation}
+w \in [0, K - S]
+\end{equation}
+Where $K$ is the number of bits received.
+\begin{equation}
+d_{i,w} = \sum_{k=0}^{N-1}\epsilon_{i-k} \sum_{s_1=0}^{S-1} \sum^{S-1}_{s_2=0} \gamma_{s_2} \gamma_{S-1-s_1} V_{i,w+s_2}^{(k, s_1 + s_2 + w)}
+\end{equation}
+
+\begin{equation}
+d_{i,w} = \sum_{k=0}^{N-1}\epsilon_{i-k} \sum_{s_1=0}^{S-1} \sum^{S-1}_{s_2=0} \gamma_{s_1} \gamma_{s_2} V_{i,w+s_2}^{(k, S - 1 - s_1 + s_2 + w)}
+\end{equation}
+In order to get rid of half overlapping range gates we use
+\begin{equation}
+V^{(k,s)}_{i,w} = X^{(L, k, s)}_{i,w} + X^{(U, k, s + 1)}_{i,w}
+\end{equation}
+with
+\begin{equation}
+\left\langle \left( X^{(z_1, k, s_1)}_{i_1,w_1} \right)^* X^{(z_2, k, s_2)}_{i_2,w_2} \right\rangle = \delta_{s_1,s_2}G^{(z_1, z_2, k, s_1)}_{\Delta, w_1 - w_2}
+\end{equation}
+with this we have
+\begin{align}
+\left \langle \left(V_{i_1,w_1+s_2}^{(k, S - 1 - s_1 + s_2 + w_1)} \right)^* V_{i_2,w_2+s_4}^{(k, S - 1 - s_3 + s_4 + w_2)} \right\rangle =\\
+G^{(L, L, S-1-s_1+s_2+w_1)}_{\Delta, w_1 - w_2 + s_2 - s_4} \delta_{s_2 - s_1 + w_1, s_4 - s_3 + w_2}\\
++G^{(U, U, S-s_1+s_2+w_1)}_{\Delta, w_1 - w_2 + s_2 - s_4} \delta_{s_2 - s_1 + w_1, s_4 - s_3 + w_2}\\
++G^{(L, U, S-1-s_1+s_2+w_1)}_{\Delta, w_1 - w_2 + s_2 - s_4} \delta_{s_2 - s_1 + w_1, s_4 - s_3 + w_2 + 1}\\
++G^{(U, L, S-s_1+s_2+w_1)}_{\Delta, w_1 - w_2 + s_2 - s_4} \delta_{s_2 - s_1 + w_1 + 1, s_4 - s_3 + w_2}
+\end{align}
+\begin{align}
+\left \langle \left(V_{i_1,w_1}^{(k, s_1)} \right)^* V_{i_2,w_2}^{(k, s_2)} \right\rangle=
+\left( G^{(L, L, s_1)}_{\Delta, \delta} + G^{(U, U, s_1 + 1)}_{\Delta, \delta} \right) \delta_{s_1, s_2} + G^{(L, U, s_1)}_{\Delta, \delta} \delta_{s_1, s_2 + 1} + G^{(U, L, s_1 + 1)}_{\Delta, \delta} \delta_{s_1 + 1, s_2}
+\end{align}
+
+we see that
+\begin{equation}
+\left( G^{(z_1, z_2, k, s_1)}_{i, w_1 - w_2} \right)^* = G^{(z_2, z_1, k, s_1)}_{i, w_1 - w_2}
+\end{equation}
+using this we have
+\begin{align}
+\left \langle \left(V_{i_1,w_1+s_2}^{(k, S - 1 - s_1 + s_2 + w_1)} \right)^* V_{i_2,w_2+s_4}^{(k, S - 1 - s_3 + s_4 + w_2)} \right\rangle =\\
+\left( G^{(U, U, S-s_1+s_2+w_1)}_{\Delta, w_1 - w_2 + s_2 - s_4} + G^{(L, L, S-1-s_1+s_2+w_1)}_{\Delta, w_1 - w_2 + s_2 - s_4} \right) \delta_{s_2 - s_1 + w_1, s_4 - s_3 + w_2}\\
++G^{(L, U, S-1-s_1+s_2+w_1)}_{\Delta, w_1 - w_2 + s_2 - s_4} \delta_{s_2 - s_1 + w_1, s_4 - s_3 + w_2 + 1}\\
++\left( G^{(L, U, S-s_1+s_2+w_1)}_{\Delta, w_1 - w_2 + s_2 - s_4} \right)^* \delta_{s_2 - s_1 + w_1 + 1, s_4 - s_3 + w_2}
+\end{align}
+\subsection{Modulation with fixed code, decoding first}
+\begin{equation}
+\langle m_{i_1, w_1}^* m_{i_2, w_2}\rangle = \sum_{s_1=0}^{S-1}\sum_{s_2=0}^{S-1} \gamma_{s_1} \gamma_{s_2} \left\langle \left( V^{(k, S-1-s_1 + w_1)}_{i_1, w_1} \right)^* V^{(k, S-1-s_2 + w_2)}_{i_2, w_2} \right \rangle
+\end{equation}
+
+\subsection{Modulation with alternating code}
+\begin{equation}
+m_{i,w} = \sum_{k=0}^{N-1} \epsilon_{i-k} \sum_{s=0}^{S-1} \gamma^{(k)}_{S-1-s} V^{(k, s + w)}_{i}
+\end{equation}
+\begin{equation}
+\hat{R}^{(h, w)}_\Delta = \frac{1}{L}\sum^{L-1}_{j=0}
+\epsilon_{j + \Delta}m_{j + \Delta + h, w}^*
+\epsilon_jm_{j + h, w}
+\end{equation}
+
+\begin{equation}
+\langle \hat{R}^{(h, w)}_\Delta \rangle = \frac{1}{L}
+\sum_{s_1=0}^{S-1}
+\sum_{s_2=0}^{S-1}
+\sum^{L-1}_{j=0}
+\sum_{k=0}^{N-1}
+\epsilon_{j + \Delta}
+\epsilon_{j + \Delta + h - k}\gamma^{(j + \Delta + h - k)}_{S-1-s_1}
+\epsilon_j
+\epsilon_{i - k} \gamma^{(j + h - k)}_{S-1-s_2}
+\langle \left(V^{(k, s_1 + w)}_{j + \Delta + h}\right)^* V^{(k, s_2 + w)}_{j+h} \rangle
+\end{equation}
+
+\section{The alternating codes}
+\subsection{Short lags expectation value}
+\begin{equation}
+m^{(c)}_j = \sum_{i=0}^{B-1} \epsilon^{(c)}_i V^{(c)}_{i,j} + \xi^{(c)}_j
+\end{equation}
+\begin{equation}
+\hat{R}^{(h(j_1 - k_1)}_\Delta = \frac{1}{M} \sum_{c=0}^{M-1} \epsilon^{(c)}_{k_1} \epsilon^{(c)}_{k_2} \left(m^{(c)}_{j_1}\right)^* m^{(c)}_{j_2}
+\end{equation}
+\begin{equation}
+\left\langle \hat{R}^{(j_1 - k_1)}_\Delta \right\rangle =
+\frac{1}{M} \sum_{c=0}^{M-1} \epsilon^{(c)}_{k_1} \epsilon^{(c)}_{k_2} \left\langle \left(m^{(c)}_{j_1}\right)^* m^{(c)}_{j_2} \right\rangle =
+\frac{1}{M} \sum_{i_1=0}^{B-1} \sum_{i_2=0}^{B-1} \sum_{c=0}^{M-1} \epsilon^{(c)}_{k_1} \epsilon^{(c)}_{k_2} \epsilon^{(c)}_{i_1}\epsilon^{(c)}_{i_2} \left\langle \left( V^{(c)}_{i_1,j_1}\right)^* V^{(c)}_{i_2,j_2} \right\rangle
+\end{equation}
+\begin{equation}
+\Delta = k_1 - k_2 = j_1 - j_2 > 0
+\end{equation}
+\subsection{Long lags expectation value}
+\begin{equation}
+m^{(c)}_j = \sum_{i=0}^{B-1} \epsilon^{(c)}_i V^{(c)}_{i,j} + \xi^{(c)}_j
+\end{equation}
+\begin{equation}
+\hat{R}^{(h(j_1 - k_1)}_\Delta = \frac{1}{M} \sum_{c=0}^{M-1} \epsilon^{(c)}_{k_1} \epsilon^{(c+1)}_{k_2} \left(m^{(c)}_{j_1}\right)^* m^{(c+1)}_{j_2}
+\end{equation}
+\begin{equation}
+\left\langle \hat{R}^{(j_1 - k_1)}_\Delta \right\rangle =
+\frac{1}{M} \sum_{c=0}^{M-1} \epsilon^{(c)}_{k_1} \epsilon^{(c+1)}_{k_2} \left\langle \left(m^{(c)}_{j_1}\right)^* m^{(c+1)}_{j_2} \right\rangle =
+\frac{1}{M} \sum_{i_1=0}^{B-1} \sum_{i_2=0}^{B-1} \sum_{c=0}^{M-1} \epsilon^{(c)}_{k_1} \epsilon^{(c+1)}_{k_2} \epsilon^{(c)}_{i_1}\epsilon^{(c+1)}_{i_2} \left\langle \left( V^{(c)}_{i_1,j_1}\right)^* V^{(c+1)}_{i_2,j_2} \right\rangle
+\end{equation}
+\begin{equation}
+\Delta = k_1 - k_2 = j_1 - j_2 > 0
+\end{equation}
+
+\subsection{Bias}
+the estimator is biased, due to signals coming from higher altitudes, which are caused by the pulse $c-1$
+\begin{equation}
+\left\langle \hat{R}^{(j_1 - k_1)}_\Delta \right\rangle =
+\frac{1}{M} \sum_{i_1=0}^{B-1} \sum_{i_2=0}^{B-1} \sum_{c=0}^{M-1} \epsilon^{(c)}_{k_1} \epsilon^{(c)}_{k_2} \epsilon^{(c-1)}_{i_1}\epsilon^{(c-1)}_{i_2} \left\langle \left( V^{(c-1, 1)}_{i_1,j_1}\right)^* V^{(c-1, 1)}_{i_2,j_2} \right\rangle
+\end{equation}
+SPECULATION: as the product of codes is random, we do not expect constant $1$ but $0$ with standard deviation of $1/\sqrt{B}$ for all indices for which the expectation value is not zero.
+the additional (implicit) averaging over $B$ will contribute another factor $1/\sqrt{B}$
+
+\subsection{Variance}
+\begin{equation}
+\left\langle \left| \hat{R}^{(j_1 - k_1)}_\Delta \right|^2 \right\rangle =
+\frac{1}{M^2} \sum_{c_1=0}^{M-1} \sum_{c_2=0}^{M-1}
+\epsilon^{(c_1)}_{k_1} \epsilon^{(c_1)}_{k_2}
+\epsilon^{(c_2)}_{k_1} \epsilon^{(c_2)}_{k_2}
+\left\langle
+m^{(c_1)}_{j_1} \left( m^{(c_1)}_{j_2}\right)^*
+\left(m^{(c_2)}_{j_1}\right)^* m^{(c_2)}_{j_2}
+\right\rangle
+\end{equation}
+\begin{equation}
+\mathrm{Var}\left[\hat{R}^{(j_1 - k_1)}_\Delta \right] =
+\frac{1}{M^2} \sum_{c_1=0}^{M-1} \sum_{c_2=0}^{M-1}
+\epsilon^{(c_1)}_{k_1} \epsilon^{(c_1)}_{k_2}
+\epsilon^{(c_2)}_{k_1} \epsilon^{(c_2)}_{k_2}
+\left\langle m^{(c_1)}_{j_1} \left(m^{(c_2)}_{j_1}\right)^* \right\rangle
+\left\langle \left(m^{(c_1)}_{j_2}\right)^* m^{(c_2)}_{j_2} \right\rangle
+\end{equation}
+\begin{equation}
+\mathrm{Var}\left[\hat{R}^{(j_1 - k_1)}_\Delta \right] \approx \frac{1}{M}
+\left\langle m^{(c)}_{j_1} \left(m^{(c)}_{j_1}\right)^* \right\rangle
+\left\langle \left(m^{(c)}_{j_2}\right)^* m^{(c)}_{j_2} \right\rangle
+\end{equation}
+\begin{equation}
+\left\langle \left(m^{(c)}_j\right)^* m^{(c)}_j \right\rangle = \sum_{i_1=0}^{B-1} \sum_{i_2=0}^{B-1} \epsilon^{(c)}_{i_1} \epsilon^{(c)}_{i_2} \left\langle V^{(c)}_{i_1,j}\left(V^{(c)}_{i_2,j}\right)^*\right\rangle + P_n \approx BP + P_n
+\end{equation}
+\begin{equation}
+\mathrm{Var}\left[\hat{R}^{(j_1 - k_1)}_\Delta \right] = \frac{(BP + P_n)^2}{M}
+\end{equation}
+
+\section{Hypothesis on code length}
 \section{Code with cyclic difference set for $\tau_i$}
